---
title: "BumblebeesSIxNN"
author: "Donna McDermott"
date: "4/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(root.dir='/tmp')
setwd("/Users/drmcder/Documents/GitHub/BumbleSIxNN")
require(ggplot2)
require(dplyr)
require(readr)
require(tidyr)
require(reshape2)
require(lme4)
require(wesanderson)
require(car)
require(binom)
require(boot)
require(tidyverse)
getwd()
```
This data was collected in April of 2019 as a follow up on last summer's social information experiment. In this experiment as in the last one, bees were tasked with foraging on two flowers over two days. On day one, their flower choices were blue (rewarding) or green (water). On day two, the same bees were placed in the same enclosures to forage on either blue (still the samelevel of reward) or purple (equally rewarding) flowers. Again, bees were assigned to different treatments with different social information cues on day one: honest (model bee on blue flower), misleading (model bee on green flower), or control (no model bee.) However, the change from my last experiments is that, this time, bees were in one of two treatments for 3 days preceding the trial: neonic-exposed and not neonic exposed. Neonic exposure (10 ppb) was through their ad. lib. supply of 1 M nectar.
Bees were taken from one of two different colonies. Both day 1 and day 2 foraging bouts lasted for 30 minutes, bees were tested independently, and 7 or 8 trials ran simulateously in the chamber at one time. 
In the colony (before testing) all bees were fed ad lib Koppert nectar solution and commercial pollen. Bees were starved for a minimim of two hours before entering foraging chamber.

Data from the 2 colonies we recieved on 2/5/19 (which were tested in the foraging chamber in March) are not included in this analysis. This is because those colonies died ~3 weeks into the experiment, with considerable decline beforehand. In early/mid march, the queens in both colonies stopped laying eggs. Soon afterwards, most bees stopped foraging when in the foraging chamber. Laura Avila and I have talked a lot about what might have happened to these colonies. I think it's most likely that the bees came in with some sort of pathogen, which spread to the other colony. We cleaned every surface we could think of with bleach before setting up the colonies we received on 3/26/19. So far, these 3/26 colonies don't exhibit the same failure to thrive.


I have also added in Data from summer 2018 (summer) and fall 2019 (October)

#Summer Data
```{r knitting data}
#importing and naming each data set
Te.1559=read.csv("foragingdata_2018.7.12.1559.csv")
colnames(Te.1559) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

sTe.1440=read.csv("foragingdata_2018.7.12.1440.csv")
colnames(sTe.1440) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1500=read.csv("foragingdata_2018.7.11.1500.csv")
colnames(Tr.1500) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

sTr.1416=read.csv("foragingdata_2018.7.11.1416.csv")
colnames(sTr.1416) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1330=read.csv("foragingdata_2018.7.11.1330.csv")
colnames(Tr.1330) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1705=read.csv("foragingdata_2018.7.5.1705.csv")
colnames(Te.1705) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1625=read.csv("foragingdata_2018.7.5.1625.csv")
colnames(Te.1625) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1507=read.csv("foragingdata_2018.7.5.1507.csv")
colnames(Te.1507) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1438=read.csv("foragingdata_2018.7.4.1438.csv")
colnames(Tr.1438) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1337=read.csv("foragingdata_2018.7.4.1337.csv")
colnames(Tr.1337) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

sTe.1702=read.csv("foragingdata_2018.6.27.1702.csv")
colnames(sTe.1702) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1607=read.csv("foragingdata_2018.6.27.1607.csv")
colnames(Te.1607) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

sTe.1518=read.csv("foragingdata_2018.6.27.1518.csv")
colnames(sTe.1518) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1635=read.csv("foragingdata_2018.6.26.1635.csv")
colnames(Tr.1635) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1518=read.csv("foragingdata_2018.6.26.1518.csv")
colnames(Tr.1518) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1434=read.csv("foragingdata_2018.6.26.1434.csv")
colnames(Tr.1434) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

#importing the data set that describes the shapes of flowers, treatment types, etc.
    #this file has a formula for changing space-separated bee id's into dash-separated bee id names
bee.info=read.csv("Donna Bombus ID Data w dashes.csv")

#knitting together data sets into "treatment" files 
sFull.Treatment1=rbind(Tr.1500,sTr.1416,Tr.1330,Tr.1438,Tr.1337,Tr.1434,Tr.1518,Tr.1635)

#knitting together data sets into "test" files
sFull.Test1=rbind(Te.1559,sTe.1440,Te.1705,Te.1625,Te.1507,sTe.1702,Te.1607,sTe.1518)


#removing tester flower from both data sets
sFull.Treatment1 =filter(sFull.Treatment1, bee !="CE-28-66-01-0B-00-12-E0")
sFull.Treatment1 =filter(sFull.Treatment1, bee !="D9-28-66-01-0B-00-12-E0")
sFull.Test1 =filter(sFull.Test1, bee !="CE-28-66-01-0B-00-12-E0")
sFull.Test1 =filter(sFull.Test1, bee !="D9-28-66-01-0B-00-12-E0")


#counting visits and rewards during Treatment runs
#tbl_df(Full.Treatment1)
sTotal.visits=count(sFull.Treatment1, bee)
#Total.visits
sTotal_Rewards=sFull.Treatment1%>%
  group_by(bee) %>%
  summarise(Rewards=sum(reward))
#Total_Rewards  

#Total_Rewards
sTotal_RV=left_join(sTotal.visits, sTotal_Rewards, by="bee")
index = which(is.na(sTotal_RV$Rewards))
sTotal_RV = sTotal_RV[-index,]
colnames(sTotal_RV)=c("bee", "Treatment.Visits", "Treatment.Rewards")
#Total_RV
sAvg.Visits=summarise(sTotal_RV, Treatment.visits=mean(Treatment.Visits), Treatment.reward=mean(Treatment.Rewards))
#Avg.Visits


#Counting visits and rewards during test runs
#tbl_df(Full.Test1)
sTotal.visitsT=count(sFull.Test1, bee)
#Total.visitsT
sTotal_RewardsT=sFull.Test1%>%
  group_by(bee) %>%
  summarise(Rewards=sum(reward))
#Total_RewardsT  

#Total_RewardsT
sTotal_RV_T=left_join(sTotal.visitsT, sTotal_RewardsT, by="bee")
index = which(is.na(sTotal_RV_T$Rewards))
sTotal_RV_T = sTotal_RV_T[-index,]
colnames(sTotal_RV_T)=c("bee", "Test.Visits", "Test.Rewards")
#Total_RV_T
sAvg.VisitsT=summarise(sTotal_RV_T, Test.visits=mean(Test.Visits), Test.reward=mean(Test.Rewards))
#Avg.VisitsT

sAllVisits=left_join(sTotal_RV,sTotal_RV_T, by="bee") %>%
  filter(Test.Visits>0)
#AllVisits
sAvg.AllVisits=cbind(sAvg.Visits, sAvg.VisitsT)
sAvg.AllVisits

sBeeData=read.csv("Donna Bombus ID Data w dashes.csv")
sBeeDataOrig=read.csv("Donna Bombus ID Data w dashes.csv")
#BeeDataOrig
#tbl_df(BeeData)
#Simple_BeeData=
 # slice(BeeData,41:109) %>%
#  group_by(bee)

sBeeData=full_join(sAllVisits, sBeeData, by="bee")
#BeeData
select(sBeeData, bee:Treatment_Type) %>%
  slice(1:50) %>%
  group_by(Treatment_Type) %>%
  summarise(AvgTreatVisits=mean(Treatment.Visits), AvgTreatRewards=mean(Treatment.Rewards),AvgTestVisits=mean(Test.Visits), AvgTestRewards=mean(Test.Rewards))

sFull.Data=rbind(sFull.Treatment1, sFull.Test1)
sdayDate= select(sFull.Data,date) %>%
  distinct(date) %>%
  slice(c(1,5,6,8,9,10))
#Full.Data

sDay=c("treatment","treatment","treatment","test","test","test")
sdayDate=cbind(sdayDate,sDay)
colnames(sdayDate)[colnames(sdayDate)=="sDay"] <- "Day"
#dayDate

colors=read.csv("Flower color data Summer SI learning envt trials.csv")
names(colors) <- c("flower", "reader", "Day", "color", "reward")
#colors

#need to join dayDate to full trial, then join treatment types and colors to all of that

sFull.Data=left_join(sFull.Data,sdayDate,by="date") 
#%>% select(-Days)
colnames(sFull.Data)[colnames(sFull.Data)=="Day.x"] <- "Day"
#Full.Data

#adding in treatment types
sFull.Data.Treatments=full_join(sFull.Data, sBeeDataOrig, by="bee")
sFull.Data.Treatments=sFull.Data.Treatments[1:40300,]
#Full.Data.Treatments
#above line is cutting out the bees from "BeeDataOrig" that we tagged (and so put on google sheet) but never tested

#adding in colors
sFull.Data.Colors=merge(sFull.Data.Treatments, colors, by=c("flower", "Day"), all=TRUE)
sFull.Data.Colors= sFull.Data.Colors[1:39600,]

#adding in a column for Colony that describes this summer data as "Colony 3", so that it can be compared in other analysis
sFull.Data.Colors=mutate(sFull.Data.Colors, Colony=3)
```

#April Data

```{r knitting data}
#importing and naming each data set

#Treatments
Tr.1416=read.csv("foragingdata_2019.4.1.1416.csv")
colnames(Tr.1416) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1506=read.csv("foragingdata_2019.4.1.1506.csv")
colnames(Tr.1506) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1557=read.csv("foragingdata_2019.4.1.1557.csv")
colnames(Tr.1557) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1636=read.csv("foragingdata_2019.4.1.1636.csv")
colnames(Tr.1636) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1141=read.csv("foragingdata_2019.4.11.1141.csv")
colnames(Tr.1141) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1240=read.csv("foragingdata_2019.4.11.1240.csv")
colnames(Tr.1240) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1340=read.csv("foragingdata_2019.4.11.1340.csv")
colnames(Tr.1340) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1327=read.csv("foragingdata_2019.4.15.1327.csv")
colnames(Tr.1327) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1408=read.csv("foragingdata_2019.4.15.1408.csv")
colnames(Tr.1408) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1447=read.csv("foragingdata_2019.4.15.1447.csv")
colnames(Tr.1447) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1538=read.csv("foragingdata_2019.4.15.1538.csv")
colnames(Tr.1538) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1623=read.csv("foragingdata_2019.4.15.1623.csv")
colnames(Tr.1623) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1324=read.csv("foragingdata_2019.4.18.1324.csv")
colnames(Tr.1324) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1404=read.csv("foragingdata_2019.4.18.1404.csv")
colnames(Tr.1404) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1450=read.csv("foragingdata_2019.4.18.1450.csv")
colnames(Tr.1450) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1538=read.csv("foragingdata_2019.4.18.1538.csv")
colnames(Tr.1538) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tr.1402=read.csv("foragingdata_2019.4.23.1402.csv")
colnames(Tr.1402) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Tr.1453=read.csv("foragingdata_2019.4.23.1453.csv")
colnames(Tr.1453) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Tr.1535=read.csv("foragingdata_2019.4.23.1535.csv")
colnames(Tr.1535) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Tr.1622=read.csv("foragingdata_2019.4.23.1622.csv")
colnames(Tr.1622) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Tr.1708=read.csv("foragingdata_2019.4.23.1708.csv")
colnames(Tr.1708) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

#Tests
Te.1404=read.csv("foragingdata_2019.4.2.1404.csv")
colnames(Te.1404) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1455=read.csv("foragingdata_2019.4.2.1455.csv")
colnames(Te.1455) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1544=read.csv("foragingdata_2019.4.2.1544.csv")
colnames(Te.1544) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1644=read.csv("foragingdata_2019.4.2.1644.csv")
colnames(Te.1644) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1247=read.csv("foragingdata_2019.4.12.1247.csv")
colnames(Te.1247) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1350=read.csv("foragingdata_2019.4.12.1350.csv")
colnames(Te.1350) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1432=read.csv("foragingdata_2019.4.12.1432.csv")
colnames(Te.1432) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1430=read.csv("foragingdata_2019.4.16.1430.csv")
colnames(Te.1430) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1509=read.csv("foragingdata_2019.4.16.1509.csv")
colnames(Te.1509) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1550=read.csv("foragingdata_2019.4.16.1550.csv")
colnames(Te.1550) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1629=read.csv("foragingdata_2019.4.16.1629.csv")
colnames(Te.1629) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1710=read.csv("foragingdata_2019.4.16.1710.csv")
colnames(Te.1710) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1440=read.csv("foragingdata_2019.4.19.1440.csv")
colnames(Te.1440) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1518=read.csv("foragingdata_2019.4.19.1518.csv")
colnames(Te.1518) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1604=read.csv("foragingdata_2019.4.19.1604.csv")
colnames(Te.1604) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1702=read.csv("foragingdata_2019.4.19.1702.csv")
colnames(Te.1702) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Te.1326=read.csv("foragingdata_2019.4.24.1326.csv")
colnames(Te.1326) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Te.1408=read.csv("foragingdata_2019.4.24.1408.csv")
colnames(Te.1408) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Te.1448=read.csv("foragingdata_2019.4.24.1448.csv")
colnames(Te.1448) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Te.1526=read.csv("foragingdata_2019.4.24.1526.csv")
colnames(Te.1526) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Te.1602=read.csv("foragingdata_2019.4.24.1602.csv")
colnames(Te.1602) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

#knitting together data sets into "treatment" files 
Full.Treatment1=rbind(Tr.1416,Tr.1506,Tr.1557,Tr.1636,Tr.1141,Tr.1240,Tr.1340,Tr.1327,Tr.1408,Tr.1447,Tr.1538,Tr.1623,Tr.1324,Tr.1404,Tr.1450,Tr.1538,Tr.1402,Tr.1453,Tr.1535,Tr.1622,Tr.1708)

#knitting together data sets into "test" files
Full.Test1=rbind(Te.1404,Te.1455,Te.1544,Te.1644,Te.1247,Te.1350,Te.1432,Te.1430,Te.1509,Te.1550,Te.1629,Te.1710,Te.1440,Te.1518,Te.1604,Te.1702,Te.1326,Te.1408,Te.1448,Te.1526,Te.1602)

#removing tester flower from both data sets
Full.Treatment1 =filter(Full.Treatment1, bee !="8E-29-66-01-0B-00-12-E0")
Full.Test1 =filter(Full.Test1, bee !="8E-29-66-01-0B-00-12-E0")
Full.Treatment1 =filter(Full.Treatment1, bee !="A2-25-66-01-0B-00-12-E0")
Full.Test1 =filter(Full.Test1, bee !="A2-25-66-01-0B-00-12-E0")

```

Adding in Bee ID data csv
This spreadsheet has info on the home colonies and treatments (both neonic and social cue) used for each bee.

  Note that this data has been transformed in Excel. First, i removed bees that dies between day 1 and day 2 trials (there were 2-3 of these, they are struck through in the original spreadsheet "Bee ID Data" on Brosi Lab Google Drive.) The RFID tag reader in the flowers and the RFID tag reader in the pen (which we use for manual input before trials) records the flower ID somewhat differently. The flower tag has dashes within the tag ID number e.g. "CE-28-66-01-0B-00-12-E0" but the pen would record the same tag as "CE 28 66 01 0B 00 00 00." I've used an excel formula in the column "bee" so that my pen readings in this spreadsheet are compatible with the foraging chamber data. Excel formula is:
  =LEFT(B2,2)&"-"&MID(B2,4,2)&"-"&MID(B2,7,2)&"-"&MID(B2,10,2)&"-"&MID(B2,13,2)&"-"&MID(B2,16,2)&"-"&"12"&"-"&"E0"

```{r BEE ID info}

BeeData=read.csv("AllApril_dashes_Bombus ID Data.csv")
#tbl_df(BeeData)
Simp_BeeData=select(BeeData, Enclosure, bee, Colony, Neonic, Treatment_Type) %>%
  slice(1:127)

```


#October Data
```{r}
#Week 1
Tre.1407=read.csv("foragingdata_2019.9.24.1407.csv")
colnames(Tre.1407) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tre.1446=read.csv("foragingdata_2019.9.24.1446.csv")
colnames(Tre.1446) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tes.1355=read.csv("foragingdata_2019.9.25.1355.csv")
colnames(Tes.1355) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tes.1438=read.csv("foragingdata_2019.9.25.1438.csv")
colnames(Tes.1438) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

#Week 2
Tre.1240=read.csv("foragingdata_2019.10.1.1240.csv")
colnames(Tre.1240) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tre.1321=read.csv("foragingdata_2019.10.1.1321.csv")
colnames(Tre.1321) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tre.1402=read.csv("foragingdata_2019.10.1.1402.csv")
colnames(Tre.1402) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tre.1439=read.csv("foragingdata_2019.10.1.1439.csv")
colnames(Tre.1439) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tre.1523=read.csv("foragingdata_2019.10.1.1523.csv")
colnames(Tre.1523) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tre.1609=read.csv("foragingdata_2019.10.1.1609.csv")
colnames(Tre.1609) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tes.1357=read.csv("foragingdata_2019.10.2.1357.csv")
colnames(Tes.1357) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tes.1437=read.csv("foragingdata_2019.10.2.1437.csv")
colnames(Tes.1437) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tes.1514=read.csv("foragingdata_2019.10.2.1514.csv")
colnames(Tes.1514) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tes.1556=read.csv("foragingdata_2019.10.2.1556.csv")
colnames(Tes.1556) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Tes.1641=read.csv("foragingdata_2019.10.2.1641.csv")
colnames(Tes.1641) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tes.1723=read.csv("foragingdata_2019.10.2.1723.csv")
colnames(Tes.1723) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

#Week 3
Tre.1312=read.csv("foragingdata_2019.10.8.1312.csv")
colnames(Tre.1312) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Tre.1352=read.csv("foragingdata_2019.10.8.1352.csv")
colnames(Tre.1352) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Tre.1433=read.csv("foragingdata_2019.10.8.1433.csv")
colnames(Tre.1433) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

Tes.1444=read.csv("foragingdata_2019.10.9.1444.csv")
colnames(Tes.1444) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Tes.1528=read.csv("foragingdata_2019.10.9.1528.csv")
colnames(Tes.1528) = c("date", "t.day", "flower", "bee", "t.forage", "reward")
Tes.1613=read.csv("foragingdata_2019.10.9.1613.csv")
colnames(Tes.1613) = c("date", "t.day", "flower", "bee", "t.forage", "reward")


#knitting together data sets into "treatment" files 
Full.TreatmentOct=rbind(Tre.1407, Tre.1446, Tre.1240, Tre.1321, Tre.1402, Tre.1439, Tre.1523, Tre.1609, Tre.1312, Tre.1352, Tre.1433)

#knitting together data sets into "test" files
Full.TestOct=rbind(Tes.1355, Tes.1438, Tes.1357, Tes.1437, Tes.1514, Tes.1556, Tes.1641, Tes.1723, Tes.1444, Tes.1528, Tes.1613)

#removing tester flower from both data sets
Full.TreatmentOct =filter(Full.TreatmentOct, bee !="A2-25-66-01-0B-00-12-E0")
Full.TestOct =filter(Full.TestOct, bee !="A2-25-66-01-0B-00-12-E0")


#counting visits and rewards during Treatment runs
#tbl_df(Full.Treatment1)
OctTotal.visits=count(Full.TreatmentOct, bee)
#Total.visits
OctTotal_Rewards=Full.TreatmentOct%>%
  group_by(bee) %>%
  summarise(Rewards=sum(reward))
#OctTotal_Rewards  

#Total_Rewards
OctTotal_RV=left_join(OctTotal.visits, OctTotal_Rewards, by="bee")
index = which(is.na(OctTotal_RV$Rewards))
OctTotal_RV = OctTotal_RV[-index,]
colnames(OctTotal_RV)=c("bee", "Treatment.Visits", "Treatment.Rewards")
#OctTotal_RV
OctAvg.Visits=summarise(OctTotal_RV, Treatment.visits=mean(Treatment.Visits), Treatment.reward=mean(Treatment.Rewards))
#OctAvg.Visits


#Counting visits and rewards during test runs
#tbl_df(Full.Test1)
OctTotal.visitsT=count(Full.TestOct, bee)
#Total.visitsT
OctTotal_RewardsT=Full.TestOct%>%
  group_by(bee) %>%
  summarise(Rewards=sum(reward))
#OctTotal_RewardsT  

#Total_RewardsT
OctTotal_RV_T=left_join(OctTotal.visitsT, OctTotal_RewardsT, by="bee")
index = which(is.na(OctTotal_RV_T$Rewards))
OctTotal_RV_T = OctTotal_RV_T[-index,]
colnames(OctTotal_RV_T)=c("bee", "Test.Visits", "Test.Rewards")
#Total_RV_T
OctAvg.VisitsT=summarise(OctTotal_RV_T, Test.visits=mean(Test.Visits), Test.reward=mean(Test.Rewards))
#OctAvg.VisitsT

OctAllVisits=left_join(OctTotal_RV,OctTotal_RV_T, by="bee") %>%
  filter(Test.Visits>0)
#AllVisits
OctAvg.AllVisits=cbind(OctAvg.Visits, OctAvg.VisitsT)
#OctAvg.AllVisits

#################Adding in data from google sheet


OctBeeData=read.csv("Bombus ID Data Oct.csv")
#OctBeeDataOrig=read.csv("Donna Bombus ID Data w dashes.csv")
#BeeDataOrig
#tbl_df(BeeData)
#Simple_BeeData=
 # slice(BeeData,41:109) %>%
#  group_by(bee)

OctBeeData=full_join(OctAllVisits, OctBeeData, by="bee")
#OctBeeData
select(OctBeeData, bee:Treatment_Type) %>%
  slice(1:66) %>%
  group_by(Treatment_Type) %>%
  summarise(AvgTreatVisits=mean(Treatment.Visits), AvgTreatRewards=mean(Treatment.Rewards),AvgTestVisits=mean(Test.Visits), AvgTestRewards=mean(Test.Rewards))

OctFull.Data=rbind(Full.TreatmentOct, Full.TestOct)

################Need to make a new DayDate
OctdayDate=read.csv("OctDayDate.csv")

#OctdayDate= select(sFull.Data,date) %>%
#  distinct(date) %>%
#  slice(c(1,5,6,8,9,10))
#Full.Data

#sDay=c("treatment","treatment","treatment","test","test","test")
#sdayDate=cbind(sdayDate,sDay)
#colnames(sdayDate)[colnames(sdayDate)=="sDay"] <- "Day"
#dayDate

colors=read.csv("Flower color data Summer SI learning envt trials.csv")
names(colors) <- c("flower", "reader", "Day", "color", "reward")
#colors

#need to join dayDate to full trial, then join treatment types and colors to all of that

OctFull.Data=left_join(OctFull.Data,OctdayDate,by="date") 
#%>% select(-Days)
colnames(OctFull.Data)[colnames(OctFull.Data)=="Day.x"] <- "Day"
#Full.Data

#adding in treatment types
OctFull.Data.Treatments=full_join(OctFull.Data, OctBeeData, by="bee")
#OctFull.Data.Treatments=sFull.Data.Treatments[1:40300,]
#Full.Data.Treatments
#above line is cutting out the bees from "BeeDataOrig" that we tagged (and so put on google sheet) but never tested

#adding in colors
OctFull.Data.Colors=merge(OctFull.Data.Treatments, colors, by=c("flower", "Day"), all=TRUE)
OctFull.Data.Colors= OctFull.Data.Colors[1:103596,]

#adding in a column for Colony that describes this fall 2019 data as "Colony 4", so that it can be compared in other analysis
OctFull.Data.Colors=mutate(OctFull.Data.Colors, Colony=4)
```


#How many visits did each bee make in its half hour treatment or test?

```{r}

#counting visits and rewards during Treatment runs
#tbl_df(Full.Treatment1)
Total.visits=count(Full.Treatment1, bee)
#Total.visits
Total_Rewards=Full.Treatment1%>%
  group_by(bee) %>%
  summarise(Rewards=sum(reward))
#Total_Rewards  

#Total_Rewards
Total_RV=left_join(Total.visits, Total_Rewards, by="bee")
index = which(is.na(Total_RV$Rewards))
Total_RV = Total_RV[-index,]
colnames(Total_RV)=c("bee", "Treatment.Visits", "Treatment.Rewards")
#Total_RV

#Counting visits and rewards during test runs
#tbl_df(Full.Test1)
Total.visitsT=count(Full.Test1, bee)
#Total.visitsT
Total_RewardsT=Full.Test1%>%
  group_by(bee) %>%
  summarise(Rewards=sum(reward))
#Total_RewardsT  

#Total_RewardsT
Total_RV_T=left_join(Total.visitsT, Total_RewardsT, by="bee")
index = which(is.na(Total_RV_T$Rewards))
Total_RV_T = Total_RV_T[-index,]
colnames(Total_RV_T)=c("bee", "Test.Visits", "Test.Rewards")
#Total_RV_T


AllVisits=full_join(Total_RV,Total_RV_T, by="bee") %>% filter(Treatment.Visits>0, Test.Visits>0)              # <--------------this makes it so you only test bees which forage on both days. to test all bees, delete this.
#AllVisits


AllBeeData=full_join(AllVisits, Simp_BeeData, by="bee") %>% filter(Treatment.Visits>0, Test.Visits>0)     

AllBeeData=group_by(AllBeeData,bee)
#BeeData
select(AllBeeData, bee:Treatment_Type) %>%
  group_by(Neonic,Treatment_Type) %>%
  summarise(AvgTreatVisits=mean(Treatment.Visits), AvgTreatRewards=mean(Treatment.Rewards),AvgTestVisits=mean(Test.Visits), AvgTestRewards=mean(Test.Rewards))
```

Thoughts: there are a lot of bees that are in BeeData with an enclosure number, etc. (127 of them) but far fewer bees (53) that show up in All Visits. I think that's because bees which never forage don't appear on the computer's data files (the ones automatically generated by the RFID tag readers.) Which means that every NA in AllBeeData (all the bees between 53 and 127) should be 0s. I've double checked, and I'm not missing any data files. A few bees were treated but not tested (like 5 or so) but that doens't explain the discrepancy, either. Also, there are no 0s in All Visits.

Ugh but actually that doesn't make a ton of sense either, becuase it means that bees either foraged during both test and treatment OR they never foraged on either day. There are no bees that foraged one day and not another. So i'm going to try removing the NA bees and see if that makes more sense.
GOing back to the AllVisits data just before doing #%>% filter(Test.Visits>0), there are ~19 bees that are treated but not tested. Which is weird becuase Total_RV_T (which groups by bee for all test day files) has 69 bees, not 72-19=53 bees.

I re-made AllVisits with a full_join instead of a left_join. This means that there are ~19 bees that have data for treatment but not test, and ~16 that have data for test but not treatment. Presumably, these NAs are 0s becuase those bees didn't forage on one day or another. I can check this in the R metadata. 

So, my options are to only evaluate bees which foraged on both days (53 bees total) or evaluate all bees, regardless of whether or not they foraged on 0,1, or 2 days (127 bees). My summer analysis used option 1. I'll try both, here, starting with bees that def foraged on both days (so, same as last time)

#Organizing total visits by flower type

Note again: The flower set up this time is exactly the same as the flower set up over the summer 2018.

```{r Flower color to GLM}
#Adding in table of types of day (test v treatment) to data

Full.Data=rbind(Full.Treatment1, Full.Test1)
dayDate= select(Full.Data,date) %>%
  distinct(date) %>% 
  slice(c(1,3,4,6,7,8,9,10,11,14))
#Full.Data

Day=c("treatment","treatment","treatment","treatment","treatment", "test","test","test","test","test")
dayDate=cbind(dayDate,Day)
#dayDate

colors=read.csv("Flower color data Summer SI learning envt trials.csv")
names(colors) <- c("flower", "reader", "Day", "color", "reward")
#colors

#need to join dayDate to full trial, then join treatment types and colors to all of that

Full.Data=left_join(Full.Data,dayDate,by="date") 
#%>% select(-Days)
colnames(Full.Data)[colnames(Full.Data)=="Day.x"] <- "Day"
#Full.Data

#adding in treatment types
Full.Data.Treatments=full_join(Full.Data, Simp_BeeData, by="bee") 
index = which(is.na(Full.Data.Treatments$t.forage))
Full.Data.Treatments = Full.Data.Treatments[-index,]
#this indexing and removal is to remove bees which did not forage on both days.

#adding in colors
Full.Data.Colors=merge(Full.Data.Treatments, colors, by=c("flower", "Day"), all=TRUE)


#make sure summer and october are inthere!
OctSlimFull.Data.Colors=OctFull.Data.Colors %>%
  select(flower, Day, date, t.day, bee, t.forage, reward.x,Enclosure,Colony,Neonic,Treatment_Type, reader, color, reward.y)

s2Full.Data.Colors=mutate(sFull.Data.Colors, Neonic="n") %>%
  select(flower, Day, date, t.day, bee, t.forage, reward.x,Enclosure,Colony,Neonic,Treatment_Type, reader, color, reward.y)

AllFull.Data.Colors=rbind(Full.Data.Colors,OctSlimFull.Data.Colors, s2Full.Data.Colors)
Trtmnt=read.csv("Trtmnt.csv")
AllFull.Data.Colors=full_join(AllFull.Data.Colors,Trtmnt, by="Treatment_Type")
#Full.Data.Colors= Full.Data.Colors[1:39600,]
#the arranging that happens here puts all the "WARNING" rows at the end of the spreadsheet. it also adds two rows, for reasons unknown. I sliced off the end of the data set to remove the WARNING rows
#Full.Data.Colors is the MOST comprehensive data set (includes more columns and a few NA values)

Full.Data.All= select(AllFull.Data.Colors, bee, Neonic, Social_Cue, reward.x, color, Day, Colony)
index = which(is.na(Full.Data.All))
Full.Data.All = Full.Data.All[-index,]
head(Full.Data.All)

#Full.Data.All removes NA's and focuses in on columns of interest.

#sum of rewards bees got from each color
color.visits=group_by(Full.Data.All, color) %>%
  summarise(Rewards=sum(reward.x))
#head(color.visits)

##making a table of colors and treatments to make analysis easier later
color.treatments=read.csv("color.treatments.csv")
color.treatments=tbl_df(color.treatments)
#color.treatments
#merging that table onto the full data
colordata=full_join(Full.Data.All, color.treatments, by="color")
#colordata
#summarizing that full data by summing up the rewards for each treatment type
sum.colordata=colordata  %>% 
  group_by(Neonic,Social_Cue, color, Colony) %>% 
  summarise(sums=sum(reward.x))
#sum.colordata
#There's some issue with sum.colordata, here, where it doesn't include the violet and green visits in the "hard" treatment. It does if you only group by treatment type and color, but then it loses them when you sum up the rewards.

treatment.summaries=spread(sum.colordata, color, sums)
#treatment.summaries
#index = which(is.na(treatment.summaries))
#treatment.summaries = treatment.summaries[-index,]
#treatment.summaries=select(treatment.summaries, blue.test, blue.treatment,green.treatment,violet.test)
#treatment.summaries


#trying to melt data using reshape2
sum.colordata=select(colordata, bee, Neonic, Social_Cue, reward.x, pre.post, new.color)
#sum.colordata
#sum.colordata is the rawest data that shows all of and each bee-flower visit.
#colorcast=dcast(sum.colordata, bee + Treatment_Type+pre.post~reward.x+new.color, fun.aggregate = sum)
#trying to just cast without melting did not work, even when I removes "reward.x"

sum.colormelt=melt(sum.colordata)
#sum.colormelt


#casting data
sum.colorcast=dcast(sum.colormelt, bee +  Neonic+ Social_Cue+pre.post~new.color, fun.aggregate = sum)
#sum.colorcast
head(sum.colorcast)
summary(sum.colorcast)
#there are some bees in here that only have one row. That's okay. I mean, it's annoying, but it's to be expected. The missing rows are due to 2 missing data files caused either by a computer glitch or a me glitch

#prepping to run G-test
b=filter(sum.colorcast, Neonic=="n")
Gtest.prep= b %>%
  group_by(Social_Cue, pre.post) %>%
  summarise(avgBlue=mean(blue), avgNotBlue=mean(not.blue))
Gtest.prep

#Berry look here for Bee Paper 1#
#G tests

require(plotrix) #for std error function

Gsumtest.prep= b %>%
  group_by(Social_Cue, pre.post) %>%
  summarise(sumBlue=sum(blue), sumNotBlue=sum(not.blue))%>%
  mutate(BlueProp=sumBlue/(sumBlue+sumNotBlue)) %>%
  mutate(BluePropSE=std.error(BlueProp))
BluePropV=as.vector(Gsumtest.prep$BlueProp)
BluePropV

Gsummatrprep=select(Gsumtest.prep, sumBlue, sumNotBlue)
gsummatr=as.matrix(Gsummatrprep, header=TRUE)
gsummatr=gsummatr[,c(2,3)]
class(gsummatr)
gsummatr

require(RVAideMemoire)
#G.test(gsummatr, p = rep(1/length(x), length(x)))
#G.test(gsummatr)
#That's not working. So maybe I should have a vector of proportions?
#require(DescTools)
obCpo=c(211,236)
obCpr=c(256, 153)
obHpo=c(155,161)
obHpr=c(261,111)
obMpo=c(213,159)
obMpr=c(195,228)
expected=c(0.5,0.5)
G.test(obCpo, expected)
#G = 1.3989, df = 1, p-value = 0.2369
G.test(obCpr, expected)
#G = 26.22, df = 1, p-value = 3.046e-07   *
G.test(obHpo, expected)
#G = 0.11393, df = 1, p-value = 0.7357
G.test(obHpr, expected)
#G = 62.24, df = 1, p-value = 3.041e-15   *
G.test(obMpo, expected)
#G = 7.8665, df = 1, p-value = 0.005036   *
G.test(obMpr, expected)
#G = 2.5771, df = 1, p-value = 0.1084

### --------------------------------------------------------------
### Crossbill example, G-test goodness-of-fit, p. 55
#gfrom https://rcompanion.org/rcompanion/b_04.html
# resource http://www.biostathandbook.com/gtestgof.html#chivsg
### --------------------------------------------------------------

#observed = c(1752, 1895)    # observed frequencies
#expected = c(0.5, 0.5)      # expected proportions

#library(DescTools)

#GTest(x=observed,
#      p=expected,
#      correct="none")            # "none" "williams" "yates"
 
#Log likelihood ratio (G-test) goodness of fit test

#G = 5.6085, X-squared df = 1, p-value = 0.01787

 


 

#GLMing data
NNapplicationGLM2=glmer(cbind(blue, not.blue)~pre.post*Neonic+(1|bee), family=binomial, data=sum.colorcast)
summary(NNapplicationGLM2)

a=filter(sum.colorcast, pre.post == "pre")
SIapplicationGLM3=glmer(cbind(blue, not.blue)~Social_Cue+(1|bee), family=binomial, data=a)
summary(SIapplicationGLM3)




######
NNxSIapplicationGLM2=glmer(cbind(blue, not.blue)~pre.post*Neonic*Social_Cue+(1|bee), family=binomial, data=sum.colorcast)
summary(NNxSIapplicationGLM2)
Anova(NNxSIapplicationGLM2)

#just the social cues, for paper #1
SIapplicationGLM2=glmer(cbind(blue, not.blue)~pre.post*Social_Cue+(1|bee), family=binomial, data=b)
summary(SIapplicationGLM2)
Anova(SIapplicationGLM2)
```


*this is the main model running and data analysis for my data, both GLMM and ANOVA

pre.postpre                        0.9902     0.1689   5.864 4.52e-09 *** (so, on average, Blue bias was pos correlated with day 1 (duh) )
Social_Cuehonest                   0.1018     0.2762   0.368    0.713    (so, across both days, honest bees were slightly (but not significantly) correlated with Blue bias )
Social_Cuemisleading               0.6333     0.2700   2.346    0.019 *  (so, across both days, midles bees and blue bias were slightly signigicantly correlated)
pre.postpre:Social_Cuehonest       0.3013     0.2561   1.176    0.239    
pre.postpre:Social_Cuemisleading  -1.6908     0.2424  -6.976 3.04e-12 *** (so, mislead bees on Day one  were NEGATIVELY correlated with blue bias compared to everyone else)

#Shit gets useful around here






Adding April and Summer Data together
And also adding in October (findme)

```{r}



#OctFull.Data.Colors

#This first step gets rid of baggage from the Bombus ID spreadsheet
#the Neonic=n in this first mutation is becuase that's summer dataa, which has no neonic data becuase that was before i started the neonic treatment

OctSlimFull.Data.Colors=OctFull.Data.Colors %>%
  select(flower, Day, date, t.day, bee, t.forage, reward.x,Enclosure,Colony,Neonic,Treatment_Type, reader, color, reward.y)

Sum.Apr.Data=rbind(s2Full.Data.Colors,Full.Data.Colors)
Sum.Apr.OctData=rbind(Sum.Apr.Data, OctSlimFull.Data.Colors)
all.colordata=full_join(Sum.Apr.OctData, color.treatments, by="color")

#checking that colony 4 is in the data
Check3=filter(all.colordata, Colony=="4")
#one of the above steps in this chunk doesnt actually have the october data. find it

#Prepping to melt data

Trtmnt=read.csv("Trtmnt.csv")
all.colordata=full_join(all.colordata,Trtmnt, by="Treatment_Type")

all.sum.colordata=all.colordata %>%
  group_by(Neonic, Treatment_Type, Colony, color)  %>%
  summarise(sums=sum(reward.x))







meltable.colordata=all.colordata %>%
  select(bee, Colony, Neonic, Social_Cue, reward.x, pre.post,new.color)


meltable.colordata$Colony <-as.character(as.numeric(meltable.colordata$Colony))

all.colormelt=melt(meltable.colordata)

all.colorcast=dcast(all.colormelt, bee+Colony+Neonic+Social_Cue+pre.post~new.color, fun.aggregate=sum)

summary(all.colorcast)

#Running models!!!
#Berry look here for Bee Paper 2

#Both days, social cues and neonic treatment on blue bias
All.NNxSI.glmm=glmer(cbind(blue,not.blue)~pre.post*Neonic*Social_Cue+(1|Colony/bee), family=binomial, data=all.colorcast)
summary(All.NNxSI.glmm)
Anova(All.NNxSI.glmm)

#> Anova(All.NNxSI.glmm)
#Analysis of Deviance Table (Type II Wald chisquare tests)

#Response: cbind(blue, not.blue)
  #                           Chisq Df Pr(>Chisq)    
#pre.post                   27.7826  1  1.357e-07 ***
#Neonic                      1.6204  1     0.2030    
#Social_Cue                  1.3303  2     0.5142    
#pre.post:Neonic             1.9463  1     0.1630    
#pre.post:Social_Cue        88.0985  2  < 2.2e-16 ***
#Neonic:Social_Cue           2.6808  2     0.2617    
#pre.post:Neonic:Social_Cue  1.9234  2     0.3822    
#---
#Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

just.neonic=all.colorcast %>%
  filter(Neonic=="y")

justneonic.NNxSI.glmm=glmer(cbind(blue,not.blue)~pre.post*Social_Cue+(1|Colony/bee), family=binomial, data=just.neonic)
summary(justneonic.NNxSI.glmm)
Anova(justneonic.NNxSI.glmm)

#just day 1, neonic (and social cue) on blue bias (Berry look here for Bee Paper 2)
just.Day1=all.colorcast %>%
  filter(pre.post=="pre")

Day1.NNxSI.glmm=glmer(cbind(blue,not.blue)~Neonic*Social_Cue+(1|Colony/bee), family=binomial, data=just.Day1)
summary(Day1.NNxSI.glmm)
Anova(Day1.NNxSI.glmm)
#no effect, but I think that's becuase the effect for misleading bees opposes the effect on honest bees

#just day 1, neonic on blue bias for misleading treatment bees

just.Day1M=just.Day1 %>%
  filter(Social_Cue=="misleading")

Day1M.NN.glmm=glmer(cbind(blue,not.blue)~Neonic+(1|Colony/bee), family=binomial, data=just.Day1M)
summary(Day1M.NN.glmm)
Anova(Day1M.NN.glmm)

just.Day1H=just.Day1 %>%
  filter(Social_Cue=="honest")

Day1H.NN.glmm=glmer(cbind(blue,not.blue)~Neonic+(1|Colony/bee), family=binomial, data=just.Day1H)
summary(Day1H.NN.glmm)
Anova(Day1H.NN.glmm)

just.Day1C=just.Day1 %>%
  filter(Social_Cue=="control")

Day1C.NN.glmm=glmer(cbind(blue,not.blue)~Neonic+(1|Colony/bee), family=binomial, data=just.Day1C)
summary(Day1C.NN.glmm)
Anova(Day1C.NN.glmm)

just.naive=all.colorcast %>%
  filter(Neonic=="n")

Check5=filter(just.naive, Colony=="4")

Colony.glmm=glmer(cbind(blue,not.blue)~pre.post*Social_Cue*Colony+(1|bee), family=binomial, data=just.naive)
summary(Colony.glmm)


#Berry look here for Bee Paper 1#
SI.glmm=glmer(cbind(blue,not.blue)~pre.post*Social_Cue+(1|Colony/bee), family=binomial, data=just.naive)
summary(SI.glmm)
Anova(SI.glmm)


#Prepping data to graph

Day12labs <- c("Day 1", "Day 2")
#+ scale_x_discrete(labels= Day12labs)


all.RewardsPerTreatment=all.colorcast %>%
  mutate(BluePreference=blue/(blue+not.blue)) %>%
  group_by(pre.post,Neonic,Social_Cue) %>%
  summarise(AvgBluePreference=mean(BluePreference), SdBluePreference=sd(BluePreference), SumBlueRewards=sum(blue), SumTotalRewards=sum(blue+not.blue)) %>%
  filter (SumBlueRewards>0)

Combo=read.csv("NN_SI_Combo.csv")

all.RewardsPerTreatment1=left_join(all.colorcast,Combo,by=c("Neonic","Social_Cue")) %>%
  mutate(BluePreference=blue/(blue+not.blue))  %>%
  group_by(pre.post,Combo, Neonic, Social_Cue) %>% 
  mutate(N=n()) %>%
  group_by(pre.post,Combo,N, Neonic, Social_Cue) %>%      #i did this to keep N as a column
  summarise(SumBlueRewards=sum(blue), SumTotalRewards=sum(blue+not.blue)) %>%
  mutate(AvgBlueRewards=SumBlueRewards/SumTotalRewards) %>%
  filter (SumBlueRewards>0)


##Calculating Confidence Intervals


all.RpTconfint=binom.confint(x=all.RewardsPerTreatment1$SumBlueRewards, n=all.RewardsPerTreatment1$SumTotalRewards, conf.level=.95, methods = "agresti-coull")
#RpTconfint
#selecting the upper and lower bounds from the conf int table to add to RewardsPerTreatment
all.RpTUpLow=select(all.RpTconfint, lower, upper )
all.RewardsPerTreatment1=bind_cols(all.RewardsPerTreatment1,all.RpTUpLow)

class(all.RewardsPerTreatment1$pre.post)
all.RewardsPerTreatment1$pre.post = factor(all.RewardsPerTreatment1$pre.post, levels(factor(all.RewardsPerTreatment1$pre.post))[c(2,1)])

#Re-ordering factors a la Alva's advice
all.RewardsPerTreatment1$Social_Cue = factor(all.RewardsPerTreatment1$Social_Cue, levels(factor(all.RewardsPerTreatment1$Social_Cue))[c(1,3,2)])

#Graphing

#Check5=filter(all.RewardsPerTreatment1, Colony=="4")

all.RewardsPerTreatment1$Combo <-as.character(as.numeric(all.RewardsPerTreatment1$Combo))

pd <- position_dodge(width = 0.1)

all.plot <- ggplot(all.RewardsPerTreatment1, aes(group=Combo, color = Combo, y = SumBlueRewards/SumTotalRewards, x = pre.post)) + geom_point( position=pd,size=1) + geom_line(aes(group = Combo), position=pd) + labs(x="Pre v Post", y="Proportion of Visits to Blue Flowers") + theme_minimal() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + coord_cartesian(xlim = c(1.4,1.9), ylim = c(0.3,0.9))+ scale_color_hue(labels=c("NN honest", "NN misleading", "NN control", "naive honest", "naive misleading", "naive control")) + geom_hline(yintercept=0.5, color = "black")
  

  
#scale_color_brewer(palette ="Set1" ) + scale_fill_discrete(name="Treatment", labels=c("NN honest", "NN misleading", "NN control", "naive honest", "naive misleading", "naive control"))

all.plot

PestiFacetLabels <- c("Not Exposed", "Pesticide Exposed")
names(PestiFacetLabels) <- c("n", "y")


# Create the plot


all.plot2 <- ggplot(all.RewardsPerTreatment1, aes(group=Social_Cue, color = Social_Cue, y = SumBlueRewards/SumTotalRewards, x = pre.post)) + geom_point( position=pd,size=3) + geom_line(aes(group = Social_Cue),, size=3, position=pd) + labs(x="Day of Foraging", y="Proportion of Visits to Blue Flowers", title="Proportion of Visits to Blue Flowers by Day") + theme_classic() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + coord_cartesian(xlim = c(1.4,1.9), ylim = c(0.3,0.9))+ scale_color_hue() + facet_grid(.~Neonic, labeller = labeller(Neonic = PestiFacetLabels)) + geom_hline(yintercept=0.5,linetype="dashed", color = "black")+scale_color_manual(values = c(control="darkgoldenrod", honest="cornflowerblue", misleading="darkolivegreen4"))




#NoPestPlot <- ggplot(all.RewardsPerTreatmentNoPesticides, aes(group=Social_Cue, color = Social_Cue, y = SumBlueRewards/SumTotalRewards, x = pre.post)) + geom_point( position=pd,size=3) + geom_line(aes(group = Social_Cue),size=3, position=pd) + labs(x="Day of Foraging", y="Proportion of Visits to Blue Flowers", title="Proportion of Visits to Blue Flowers for Bees Trained With Different Social Cues") + theme_classic() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + coord_cartesian(xlim = c(1.4,1.9), ylim = c(0.3,0.9))+ scale_color_hue() + geom_hline(yintercept=0.5,linetype="dashed", color = "black") + scale_fill_discrete(name = "Social Cue Treatment")

all.RewardsPerTreatmentNoPesticides=filter(all.RewardsPerTreatment1, Neonic=="n")
NoPestPlot <- ggplot(all.RewardsPerTreatmentNoPesticides, aes(group=Social_Cue, color = Social_Cue, y = SumBlueRewards/SumTotalRewards, x = pre.post)) + geom_point( position=pd,size=3) + geom_line(aes(group = Social_Cue),size=3, position=pd) + labs(x="Day of Foraging", y="Proportion of Visits to Blue Flowers", title="Proportion of Visits to Blue Flowers for Bees Trained With Different Social Cues") + theme_classic() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + coord_cartesian(xlim = c(1.4,1.9), ylim = c(0.3,0.9))+ scale_color_hue() + geom_hline(yintercept=0.5,linetype="dashed", color = "black") + scale_color_hue(name="Social Cue Treatment")

NoPestPlot
#Repeating the above graphing + prep with the non-exposed bees
naive.RewardsPerTreatment=just.naive %>%
  mutate(BluePreference=blue/(blue+not.blue)) %>%
  group_by(pre.post,Social_Cue, Colony) %>%
  summarise( SumBlueRewards=sum(blue), SumTotalRewards=sum(blue+not.blue)) %>%
  filter (SumBlueRewards>0)

Check5=filter(naive.RewardsPerTreatment, Colony=="4")


naive.RpTconfint=binom.confint(x=naive.RewardsPerTreatment$SumBlueRewards, n=naive.RewardsPerTreatment$SumTotalRewards, conf.level=.95, methods = "agresti-coull")

naive.RpTUpLow=select(naive.RpTconfint, lower, upper )
naive.RewardsPerTreatment=bind_cols(naive.RewardsPerTreatment,naive.RpTUpLow)

naive.RewardsPerTreatment$pre.post = factor(naive.RewardsPerTreatment$pre.post, levels(factor(naive.RewardsPerTreatment$pre.post))[c(2,1)])

naive.RewardsPerTreatment$Social_Cue = factor(naive.RewardsPerTreatment$Social_Cue, levels(factor(naive.RewardsPerTreatment$Social_Cue))[c(1,3,2)])

Check5=filter(naive.RewardsPerTreatment, Colony=="4")

naive.plot <- ggplot(naive.RewardsPerTreatment, aes(group=Social_Cue, color = Social_Cue, y = SumBlueRewards/SumTotalRewards, x = pre.post)) + geom_point( position=pd,size=3) + geom_line(aes(group = Social_Cue), position=pd) + labs(x="Pre v Post", y="Proportion of Visits to Blue Flowers") + theme_classic() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + coord_cartesian(xlim = c(1.4,1.9), ylim = c(0.2,0.9))+ scale_color_hue() + facet_grid(.~Colony)+scale_color_manual(values = c(control="darkgoldenrod", honest="cornflowerblue", misleading="darkolivegreen3"))

naive.plot

NoPestPlot <- ggplot(all.RewardsPerTreatmentNoPesticides, aes(group=Social_Cue, color = Social_Cue, y = SumBlueRewards/SumTotalRewards, x = pre.post)) + geom_point( position=pd,size=3) + geom_line(aes(group = Social_Cue),size=3, position=pd) + labs(x="Day of Foraging", y="Proportion of Visits to Blue Flowers", title="Proportion of Visits to Rewarding Flowers with Social Cue Training") + theme_classic() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + coord_cartesian(xlim = c(1.4,1.9), ylim = c(0.3,0.9))+ scale_color_hue() + geom_hline(yintercept=0.5,linetype="dashed", color = "black") + scale_fill_discrete(name = "Social Cue Treatment")+scale_color_manual(values = c(control="darkgoldenrod", honest="cornflowerblue", misleading="darkolivegreen4")) + scale_x_discrete(labels= Day12labs)


#all the same but just for pre
pre.RewardsPerTreatment=filter(all.RewardsPerTreatment1, pre.post=="pre")

pre.plot <-ggplot(pre.RewardsPerTreatment, aes(group=Neonic, color=Neonic, y=SumBlueRewards/SumTotalRewards, x=Social_Cue))+ geom_point( position=pd,size=3)  + labs(x="Social Cue", y="Proportion of Visits to Blue Flowers", title="Visits to Reward Flower on Day 1 by Neonicotinoid Exposure") + theme_classic() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + scale_color_hue() + scale_color_hue(name="Pesticide Exposure", labels=c("Not Exposed", "Exposed")) + geom_hline(yintercept=0.5,linetype="dashed", color = "black") + scale_color_manual(values = c(y="green3", n="lightslategrey"), name="Pesticide Exposure", labels=c("Not Exposed", "Exposed"))

post.RewardsPerTreatment=filter(all.RewardsPerTreatment1, pre.post=="post")
post.plot <-ggplot(post.RewardsPerTreatment, aes(group=Neonic, color=Neonic, y=SumBlueRewards/SumTotalRewards, x=Social_Cue))+ geom_point( position=pd,size=1)  + labs(x="Social Cue", y="Proportion of Visits to Blue Flowers") + theme_minimal() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + scale_color_hue() + scale_color_hue(name="Pesticide Exposure", labels=c("Not Exposed", "Exposed"))

#scale_color_manual(values = c(y="lawngreen", n="lightslategrey"))
#these are the colors I want, but if I add them as-is I overwrite the naming of y and n. Figure that out later.

post.plot

all.plot2

#OKAY SO IT LOOKS LIKE
NoPestPlot
#Is the one to look at to compare how misleading cues are different than honest cues #and post.plot shows this as well, tbh
pre.plot
#Is the one to look at to compare NN to not-NN. It's only about day 1


```


#Test of Homogeneity of Variance
Are the Neonic bees (across social cue treatments) more similar to one another than the not-neonic bees?
^A way of getting at the question- are  all the pesticide exposed bees acting the same?


```{r}
#need a data set that pools all the per-bee data for NN and not-NN, but separates all of that out by colony (since test can't account for non-independence of bees related by colony)

pre.colorcast= all.colorcast %>%
  filter(pre.post=="pre") %>%
  mutate(BluePref=blue/(blue+not.blue))

Col1.pre= filter(pre.colorcast, Colony==1)
#n=45
Col2.pre=filter(pre.colorcast,Colony==2)
#n=52
Col3.pre=filter(pre.colorcast, Colony==3)
#n=61
Col4.pre=filter(pre.colorcast, Colony==4)
#n=71
#pre.colorcast has a few NAs in it, which is why theses n's add up to 229 but pre.colorcast has 232 rows

#fligner-Killeen test
require(stats)
fligner.test(BluePref~Neonic, pre.colorcast)
#data:  BluePref by Neonic
#Fligner-Killeen:med chi-squared = 0.2373, df = 1, p-value = 0.6262

#Colony 1
fligner.test(BluePref~Neonic, Col1.pre)
#Colony 2
fligner.test(BluePref~Neonic, Col2.pre)
#Colony 3
fligner.test(BluePref~Neonic, Col3.pre)
#Colony 4
fligner.test(BluePref~Neonic, Col4.pre)

#none are sig differemt

t=filter(Col1.pre, Neonic=="y")
#21
tn=filter(Col1.pre, Neonic=="n")
#24
t2=filter(Col2.pre, Neonic=="y")
#24
t2n=filter(Col2.pre, Neonic=="n")
#28
t3=filter(Col3.pre, Neonic=="y")  #**Can I even include colony 3 in this?
#0
t3n=filter(Col3.pre, Neonic=="n")
#61
t4=filter(Col4.pre, Neonic=="y")
#34
t4n=filter(Col4.pre, Neonic=="n")
#35

```
Results of fligner tests by colony:
> #Colony 1
> fligner.test(BluePref~Neonic, Col1.pre)

	Fligner-Killeen test of homogeneity of variances

data:  BluePref by Neonic
Fligner-Killeen:med chi-squared = 0.062827, df = 1, p-value = 0.8021

> #Colony 2
> fligner.test(BluePref~Neonic, Col2.pre)

	Fligner-Killeen test of homogeneity of variances

data:  BluePref by Neonic
Fligner-Killeen:med chi-squared = 0.063218, df = 1, p-value = 0.8015

> #Colony 3
> fligner.test(BluePref~Neonic, Col3.pre)
Error in fligner.test.default(c(0.5, 0.619047619047619, 0.545454545454545,  : 
  all observations are in the same group
> #Colony 4
> fligner.test(BluePref~Neonic, Col4.pre)

	Fligner-Killeen test of homogeneity of variances

data:  BluePref by Neonic
Fligner-Killeen:med chi-squared = 0.060475, df = 1, p-value = 0.8057




#How many bees?
```{r}
#overall
totalbees=count(all.colordata, bee)
#totalbees=259

#no pesticides total
totalNoPest= all.colordata %>% 
  filter(Neonic=="n") %>%
  count(bee)
#totalNoPest=170

#Pesticides total
totalPest= all.colordata %>% 
  filter(Neonic=="y") %>%
  count(bee)
#totalPest=86


#control, no 
ControlNoPest= all.colordata %>% 
  filter(Neonic=="n") %>%
  filter(Social_Cue=="control") %>%
  count(bee)
#ControlNoPest = 56
#control, yes
ControlPest= all.colordata %>% 
  filter(Neonic=="y") %>%
  filter(Social_Cue=="control") %>%
  count(bee)
#ControlPest=30


#honest, no
HonestNoPest= all.colordata %>% 
  filter(Neonic=="n") %>%
  filter(Social_Cue=="honest") %>%
  count(bee)
#HonestNoPest = 55
#honest, yes
HonestPest= all.colordata %>% 
  filter(Neonic=="y") %>%
  filter(Social_Cue=="honest") %>%
  count(bee)
#HonestPest=30

#miselading, no
MislNoPest= all.colordata %>% 
  filter(Neonic=="n") %>%
  filter(Social_Cue=="misleading") %>%
  count(bee)
#MislNoPest=58
#misleading, yes
MislPest= all.colordata %>% 
  filter(Neonic=="y") %>%
  filter(Social_Cue=="misleading") %>%
  count(bee)
#MislPest=26
```



#Reward Differences
How did treatments affect how "well" the bees did?

As of April 2 2020 this whole section is a mess because of some issue with boot.ci. It worked before though so ahhhhhhhhhhhhhhhhhhhh.

```{r}
#here's some code for the modeling
#NNxSIapplicationGLM2=glmer(cbind(blue, not.blue)~pre.post*Neonic*Social_Cue+(1|bee), family=binomial, data=sum.colorcast)
#summary(NNxSIapplicationGLM2)
#Anova(NNxSIapplicationGLM2)

#SameDay1OrderPlot=ggplot(data=Spread.Day1order, aes(group=Treatment_Type, color=Treatment_Type, x=Order, y=BluePref)) + facet_grid(.~Neonic) + geom_point(position=pd, size=1) + geom_line(aes(group=Treatment_Type), position=pd) +theme_classic() + coord_cartesian(xlim = c(1,5))+ labs(title="Bees' Preference for Blue Flowers on Day 1, Choices 1-5")
#SameDay1OrderPlot

#Start with day 1- did bees get different numbers of rewards overall? use dataframe a, which is a filter for pre on sum.colorcast

RewardsPre=a %>%
  group_by(Neonic,Social_Cue) %>%
  summarise(MeanRewards=mean(blue), SdRewards=sd(blue), SumRewards=sum(blue))

#BeeCount=a2 %>%
#  group_by(Neonic, Social_Cue) %>%
#  count(bee)
#that's not right...


#I'm not sure if SumBlue is right here- do I want the number of bees in each treatment, or the number of rewards in each treatment? I have rewards now, becuase that's easier. I thin I want bees.

#confidence intervals  <----------------Ask Berry about this
#mean=RewardsPre$BlueRewards
#sd=SdBlue
#n=number of bees in each treatment group?


RewardsPreLM=lm(blue~Neonic*Social_Cue, data=a)
summary(RewardsPreLM)

RewardsPrePlot=ggplot(data=RewardsPre, aes(x=Social_Cue, y=MeanRewards, group=Neonic, color=Neonic)) + geom_point() +geom_line() +theme_classic()
RewardsPrePlot



#And similar for post data

b=filter(sum.colorcast, pre.post == "post") %>%
  mutate(Rewards=blue+not.blue)

RewardsPostlm=lm(Rewards~Neonic*Social_Cue, data=b)
summary(RewardsPostlm)


RewardsPost=b %>% 
  group_by(Neonic,Social_Cue) %>%
  summarise(MeanRewards=mean(Rewards), SdRewards=sd(Rewards), SumRewards=sum(Rewards))

RewardsPostPlot=ggplot(data=RewardsPost, aes(x=Social_Cue, y=MeanRewards, group=Neonic, color=Neonic)) + geom_point() +geom_line() +theme_classic() 
RewardsPostPlot

#adding in confidence intervals
#poisson.test(c$MeanRewards, conf.level = 0.95 )$conf.int
#confidence intervals need to be added to data that includes all bees, like sum.colorcast. but, becuase "rewards" means differnt things to pre and post data (i.e just blue or blue &green), confidence intervals need to be calculated separately (in a2 for pre and b for post)

# function below taken from https://stats.stackexchange.com/questions/10926/how-to-calculate-confidence-interval-for-count-data-in-r
exactPoiCI <- function (X, conf.level=0.95) {
  alpha = 1 - conf.level
  upper <- 0.5 * qchisq((1-(alpha/2)), (2*X))
  lower <- 0.5 * qchisq(alpha/2, (2*X +2))
  return(c(lower, upper)) }

a2=mutate(a, Rewards=blue+0)
a2=a2 %>% 
   rowwise %>%
   mutate(ConfintLow = exactPoiCI(Rewards)[1], ConfintHigh=exactPoiCI(Rewards)[2]) 
b=b %>% 
   rowwise %>%
   mutate(ConfintLow = exactPoiCI(Rewards)[1], ConfintHigh=exactPoiCI(Rewards)[2]) 

#selecting the upper and lower bounds from the conf int table to add to RewardsPerTreatment
#RpTUpLow=select(RpTconfint, lower, upper )
#RewardsPerTreatment2=bind_cols(RewardsPerTreatment2,RpTUpLow)
#index = which(is.na(RewardsPerTreatment2$Combo))
#RewardsPerTreatment2 = RewardsPerTreatment2[-index,]


BootCI=read.csv("bootCI.SIxNN.csv")
FlowerAvgBootCI=read.csv("FlowerAvgbootCI.SIxNN.csv")


#cutting the "post" value of the last figure in half because 2 flowers.
FlowerNumber=data.frame(c("pre","post"), c(1,2))
colnames(FlowerNumber)=(c("pre.post","FlowerNumber"))
FlowerNumber

#all on one graph?

c=rbind(a2,b) 
c=full_join(c, FlowerNumber)

c2=c %>%
  group_by(Neonic,Social_Cue, pre.post) %>%
  mutate(AvgRewards=Rewards/FlowerNumber) %>%
  summarise(MeanRewards=mean(Rewards), SdRewards=sd(Rewards), SumRewards=sum(Rewards), MeanLow=mean(ConfintLow), MeanHigh=mean(ConfintHigh)) 

Categories=c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j", "k", "l", "m", "n")
Categories=data.frame(Categories)
c2=bind_cols(c2,Categories)
c2=slice(c2, 1:5)
c2=filter(c2, SumRewards > 12)

class(c2$pre.post)
c2$pre.post = factor(c2$pre.post, levels(factor(c2$pre.post))[c(2,1)])

RewardsPlot=ggplot(data=c2, aes(x=pre.post, y=MeanRewards, group=Neonic, color=Neonic)) + geom_point() +geom_line() +theme_classic() +facet_grid(.~Social_Cue) 

#+ geom_errorbar(aes(ymin=MeanLow, ymax=MeanHigh, width=.1))
RewardsPlot

#ahh ffs it's overdispersed with regular poisson confidence intervals

#trying to make some confidence intervals using negative binomial model
#require(glmmTMB)

#m <- glmmTMB(
#  MeanRewards ~ Categories,
#  ziformula = ~ 0,
#  family = truncated_nbinom1,
#  data = c2
#)
#summary(m)
#SugarCI=confint(m) #this in confint on my model coefficient,not estimates (the meanrewards)
#SugarCI=as.data.frame(SugarCI)
#SugarCI
#selecting the upper and lower bounds from the conf int table to add to RewardsPerTreatment
#SugarUpLow=select(SugarCI, "2.5 %", "97.5 %") %>%
#  slice(1:14)
#SugarUpLow
#c2=bind_cols(c2,SugarUpLow)
#index = which(is.na(RewardsPerTreatment2$Combo))
#RewardsPerTreatment2 = RewardsPerTreatment2[-index,]

#QuasiPOsisson GLM?
#i should be running 
RewardsQPglm <- glm(Rewards ~ Neonic*Social_Cue*pre.post, quasipoisson, data=c)
summary(RewardsQPglm)
#ANOVA
#Anova(RewardsQPglm)
#Analysis of Deviance Table (Type II tests)

#Response: Rewards
#                           LR Chisq Df Pr(>Chisq)    
#Neonic                        0.034  1    0.85329    
#Social_Cue                    6.389  2    0.04098 *  
#pre.post                     69.981  1    < 2e-16 ***
#Neonic:Social_Cue             0.640  2    0.72616    
#Neonic:pre.post               1.843  1    0.17457    
#Social_Cue:pre.post           5.120  2    0.07730 .  
#Neonic:Social_Cue:pre.post    2.964  2    0.22716    
#---
#Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

#need a package that does confidence intervals for my estimates (meanrewards), like binom.confint (ended up using boot, at top)
ratio <- function(d, w) sum(d$x * w)/sum(d$u * w)
city.boot <- boot(city, ratio, R = 999)
#boot.ci(city.boot, conf = c(0.90, 0.95),
#        type = "bca")

#get ready for how obnoxious this is

#No Pesticides, Honest Social Cues, Pre
cNPreHon=filter(c, Neonic=="n", pre.post=="pre", Social_Cue=="honest")
cNPreHon=cNPreHon$Rewards
samplemean <- function(cNPreHon, d) {
  return(mean(cNPreHon[d]))
}
Nprehon.boot=boot(cNPreHon, samplemean, R=999)

boot.ci(Nprehon.boot, conf=0.95, type="bca")
#95%   ( 4.722,  6.739 )  

#No Pesticides, Honest Social Cues, Post
cNPoHon=filter(c, Neonic=="n", pre.post=="post", Social_Cue=="honest")
cNPoHon=cNPoHon$Rewards
samplemean2 <- function(cNPoHon, d) {
  return(mean(cNPoHon[d]))
}
Npohon.boot=boot(cNPoHon, samplemean, R=999)

boot.ci(Npohon.boot, conf=0.95, type="bca")
#95%   ( 5.590,  7.841 ) 

#No Pesticides, Misleading Social Cues, Post
cNPoM=filter(c, Neonic=="n", pre.post=="post", Social_Cue=="misleading")
cNPoM=cNPoM$Rewards
samplemean2 <- function(cNPoM, d) {
  return(mean(cNPoM[d]))
}
NpoM.boot=boot(cNPoM, samplemean, R=999)

boot.ci(NpoM.boot, conf=0.95, type="bca")
#95%   ( 6.200,  8.697 )

#No Pesticides, Misleading Social Cues, Pre
cNPrM=filter(c, Neonic=="n", pre.post=="pre", Social_Cue=="misleading")
cNPrM=cNPrM$Rewards
samplemean2 <- function(cNPrM, d) {
  return(mean(cNPrM[d]))
}
NprM.boot=boot(cNPrM, samplemean, R=999)

boot.ci(NprM.boot, conf=0.95, type="bca")
#95%   ( 2.827,  4.846 ) 

#No Pesticides, Control Social Cues, Pre
cNPrC=filter(c, Neonic=="n", pre.post=="pre", Social_Cue=="control")
cNPrC=cNPrC$Rewards
samplemean2 <- function(cNPrC, d) {
  return(mean(cNPrC[d]))
}
NprC.boot=boot(cNPrC, samplemean, R=999)
boot.ci(NprC.boot, conf=0.95, type="bca")
#95%   ( 4.143,  6.184 ) 

#No Pesticides, Control Social Cues, Post
cNPoC=filter(c, Neonic=="n", pre.post=="post", Social_Cue=="control")
cNPoC=cNPoC$Rewards
samplemean2 <- function(cNPoC, d) {
  return(mean(cNPoC[d]))
}
NpoC.boot=boot(cNPoC, samplemean, R=999)
boot.ci(NpoC.boot, conf=0.95, type="bca")
#95%   ( 7.569,  9.961 )  

#No Pesticides, Control Social Cues, Post
cNPoC=filter(c, Neonic=="n", pre.post=="post", Social_Cue=="control")
cNPoC=cNPoC$Rewards
samplemean2 <- function(cNPoC, d) {
  return(mean(cNPoC[d]))
}
NpoC.boot=boot(cNPoC, samplemean, R=999)
boot.ci(NpoC.boot, conf=0.95, type="bca")
#95%   ( 7.569,  9.961 )  


#Yes, did use pesticides below

#YesPesticides, Honest Social Cues, Pre
cYPreHon=filter(c, Neonic=="y", pre.post=="pre", Social_Cue=="honest")
cYPreHon=cYPreHon$Rewards
samplemean <- function(cYPreHon, d) {
  return(mean(cYPreHon[d]))
}
Yprehon.boot=boot(cYPreHon, samplemean, R=999)

boot.ci(Yprehon.boot, conf=0.95, type="bca")
#95%   ( 3.216,  5.704 ) 

#Yes Pesticides, Honest Social Cues, Post
cYPoHon=filter(c, Neonic=="y", pre.post=="post", Social_Cue=="honest")
cYPoHon=cYPoHon$Rewards
samplemean2 <- function(cYPoHon, d) {
  return(mean(cYPoHon[d]))
}
Ypohon.boot=boot(cYPoHon, samplemean, R=999)

boot.ci(Ypohon.boot, conf=0.95, type="bca")
#95%   ( 6.793,  9.862 ) 

#Yes Pesticides, Misleading Social Cues, Post
cYPoM=filter(c, Neonic=="y", pre.post=="post", Social_Cue=="misleading")
cYPoM=cYPoM$Rewards
samplemean2 <- function(cYPoM, d) {
  return(mean(cYPoM[d]))
}
YpoM.boot=boot(cYPoM, samplemean, R=999)

boot.ci(YpoM.boot, conf=0.95, type="bca")
#95%   ( 6.05,  9.55 ) 

#Yes Pesticides, Misleading Social Cues, Pre
cYPrM=filter(c, Neonic=="y", pre.post=="pre", Social_Cue=="misleading")
cYPrM=cYPrM$Rewards
samplemean2 <- function(cYPrM, d) {
  return(mean(cYPrM[d]))
}
YprM.boot=boot(cYPrM, samplemean, R=999)

boot.ci(YprM.boot, conf=0.95, type="bca")
#95%   ( 2.458,  5.917 )  

#yes Pesticides, Control Social Cues, Pre
cYPrC=filter(c, Neonic=="y", pre.post=="pre", Social_Cue=="control")
cYPrC=cYPrC$Rewards
samplemean2 <- function(cYPrC, d) {
  return(mean(cYPrC[d]))
}
YprC.boot=boot(cYPrC, samplemean, R=999)
boot.ci(YprC.boot, conf=0.95, type="bca")
#95%    ( 3.857,  5.893 )  

#yes Pesticides, Control Social Cues, Post
cYPoC=filter(c, Neonic=="y", pre.post=="post", Social_Cue=="control")
cYPoC=cYPoC$Rewards
samplemean2 <- function(cYPoC, d) {
  return(mean(cYPoC[d]))
}
YpoC.boot=boot(cYPoC, samplemean, R=999)
boot.ci(YpoC.boot, conf=0.95, type="bca")
#95%  ( 6.458,  9.348 )




#plot but now with confidence intervals
c3=full_join(c2, BootCI)
c3=full_join(c3, FlowerAvgBootCI)

#making a lil' dataframe to that assigns pre to one flower and post to two flowers
FlowersNumber=c(1,2)
pre.post=c("pre","post")
FlowerNumbByDay <- data.frame(pre.post, FlowersNumber, stringsAsFactors=FALSE)
c3=full_join(c3,FlowerNumbByDay)

c3=mutate(c3, AvgPrePost= MeanRewards/FlowersNumber)
class(c3$pre.post)
c3$pre.post = factor(c3$pre.post, levels(factor(c3$pre.post))[c(2,1)])

RewardsPlotCI=ggplot(data=c3, aes(x=pre.post, y=MeanRewards, group=Neonic, color=Neonic)) + geom_point() + geom_line() +theme_classic() +facet_grid(.~Social_Cue)+ geom_errorbar(aes(ymin=bootLO, ymax=bootHI, width=.1), position=pd)

#+ geom_errorbar(aes(ymin=MeanLow, ymax=MeanHigh, width=.1))
RewardsPlotCI




RewardsPlotAvgd=ggplot(data=c3, aes(x=pre.post, y=AvgPrePost, group=Neonic, color=Neonic)) + geom_point() + geom_line() +theme_classic() +facet_grid(.~Social_Cue)

#geom_errorbar(aes(ymin=bootLO, ymax=bootHI, width=.1), position=pd)

RewardsPlotAvgd

#re-doing CI for post values that are now halved



#yes Pesticides, Control Social Cues, Post
cYPoC=filter(c, Neonic=="y", pre.post=="post", Social_Cue=="control")
cYPoC=cYPoC$AvgRewards
samplemean2 <- function(cYPoC, d) {
  return(mean(cYPoC[d]))
}
#YpoC.boot=boot(cYPoC, samplemean, R=999)
boot.ci(YpoC.boot, conf=0.95, type="bca")
#95%  95%   ( 3.304,  4.804 ) 

#Yes Pesticides, Honest Social Cues, Post
cYPoHon=filter(c, Neonic=="y", pre.post=="post", Social_Cue=="honest")
cYPoHon=cYPoHon$AvgRewards
samplemean2 <- function(cYPoHon, d) {
  return(mean(cYPoHon[d]))
}
#Ypohon.boot=boot(cYPoHon, samplemean, R=999)

boot.ci(Ypohon.boot, conf=0.95, type="bca")
#95%   ( 3.431,  5.034 )  

#Yes Pesticides, Misleading Social Cues, Post
cYPoM=filter(c, Neonic=="y", pre.post=="post", Social_Cue=="misleading")
cYPoM=cYPoM$AvgRewards
samplemean2 <- function(cYPoM, d) {
  return(mean(cYPoM[d]))
}
#YpoM.boot=boot(cYPoM, samplemean, R=999)

boot.ci(YpoM.boot, conf=0.95, type="bca")
#95%    ( 3.077,  4.750 ) 


#No Pesticides, Control Social Cues, Post
cNPoC=filter(c, Neonic=="n", pre.post=="post", Social_Cue=="control")
cNPoC=cNPoC$AvgRewards
samplemean2 <- function(cNPoC, d) {
  return(mean(cNPoC[d]))
}
#NpoC.boot=boot(cNPoC, samplemean, R=999)
boot.ci(NpoC.boot, conf=0.95, type="bca")
#95%   ( 3.826,  5.000 ) 

#No Pesticides, Honest Social Cues, Post
cNPoHon=filter(c, Neonic=="n", pre.post=="post", Social_Cue=="honest")
cNPoHon=cNPoHon$AvgRewards
samplemean2 <- function(cNPoHon, d) {
  return(mean(cNPoHon[d]))
}
#Npohon.boot=boot(cNPoHon, samplemean, R=999)

boot.ci(Npohon.boot, conf=0.95, type="bca")
#95%   ( 2.852,  3.884 )  

#No Pesticides, Misleading Social Cues, Post
cNPoM=filter(c, Neonic=="n", pre.post=="post", Social_Cue=="misleading")
cNPoM=cNPoM$AvgRewards
samplemean2 <- function(cNPoM, d) {
  return(mean(cNPoM[d]))
}
#NpoM.boot=boot(cNPoM, samplemean, R=999)

boot.ci(NpoM.boot, conf=0.95, type="bca")
#95%   ( 3.10,  4.36 ) 




pre.plot <-ggplot(pre.RewardsPerTreatment, aes(group=Neonic, color=Neonic, y=SumBlueRewards/SumTotalRewards, x=Social_Cue))+ geom_point( position=pd,size=3)  + labs(x="Social Cue", y="Proportion of Visits to Blue Flowers", title="Proportion of Visits to Blue Flowers on Day 1 by Neonicotinoid Exposure") + theme_classic() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + scale_color_hue() + scale_color_hue(name="Pesticide Exposure", labels=c("Not Exposed", "Exposed")) + geom_hline(yintercept=0.5,linetype="dashed", color = "black")


RewardsPlotAvgdCI=ggplot(data=c3, aes(x=pre.post, y=AvgPrePost, group=Neonic, color=Neonic)) + geom_point(size=3) + geom_line(size=3) +theme_classic() +facet_grid(.~Social_Cue)+ geom_errorbar(aes(ymin=AvgbootLO, ymax=AvgbootHI, width=.1), position=pd) + scale_color_hue(name="Pesticide Exposure", labels=c("Not Exposed", "Exposed")) + labs(x="Day of Foraging", y="Amount of Sugar-Water Received per Rewarding Flower", title="Number of Sugar-Water Rewards Received") + scale_color_manual(values = c(y="green3", n="lightslategrey"), name="Pesticide Exposure", labels=c("Not Exposed", "Exposed"))

#geom_errorbar(aes(ymin=bootLO, ymax=bootHI, width=.1), position=pd)

RewardsPlotAvgdCI



```



#Committe Member Questions from back in the day
Chris asked: You talked about the interaction effect.  If you just look at the pre data, is there a significant
effect of treatment, especially if you compare the control to the blue flower with dead bee?  In other words, can you replicate the effect of social cues?

Berry interprets this as 









{r permutation test}
#require(coin)      #can't use coin without new r version. the p values as written only represent summer and april data, not october data
#require(FSA)
#http://rcompanion.org/handbook/K_01.html
#Summarize(Length ~ Hand,   data=Data,   digits=3)

#   Hand  n nvalid   mean    sd  min    Q1 median    Q3  max percZero
#1  Left 16     16 17.356 1.948 13.5 16.35  17.50 18.52 21.1        0
#2 Right 16     16 17.594 1.972 13.7 16.35  17.55 18.90 21.5        0
#independence_test(Length ~ Hand, data = Data)

#On Day 1, do different social cues yield different reward levels?
independence_test(Rewards~Social_Cue, data=a2) #p=.025
independence_test(Rewards~Neonic, data=a2) #p=.3131


a2Honest=filter(a2, Social_Cue == "honest")
independence_test(Rewards~Neonic, data=a2Honest) #p=.079

a2control=filter(a2, Social_Cue == "control")
independence_test(Rewards~Neonic, data=a2control) #p=.605

a2misleading=filter(a2, Social_Cue == "misleading")
independence_test(Rewards~Neonic, data=a2misleading) #p=.861

#On Day 2, do different social cues yield different reward levels?
independence_test(Rewards~Social_Cue, data=b) #p=.1288
independence_test(Rewards~Neonic, data=b) #p=.5057


bHonest=filter(b, Social_Cue == "honest")
independence_test(Rewards~Neonic, data=bHonest) #p=.1369

bcontrol=filter(b, Social_Cue == "control")
independence_test(Rewards~Neonic, data=bcontrol) #p=.5391

bmisleading=filter(b, Social_Cue == "misleading")
independence_test(Rewards~Neonic, data=bmisleading) #p=.6911




















#graphs on graphs
I'm pretty sure this whole section only has April Data, while sections above have data from all trials.
i.e. this secton is kinda worthless

``{r graphs and CIs}

#putting summary stats in sum.colordata so I can plot them

#head(sum.colordata)

color.visits=group_by(Full.Data.All, color) %>%
  summarise(Rewards=sum(reward.x))

RewardsPerBee=sum.colordata %>%
  group_by(Treatment_Type,pre.post, bee, new.color)%>%
  summarise(TotalReward=sum(reward.x)) %>%
  arrange(bee)

#RewardsPerBee

#need to cast this so that last two columns are blue column and not blue column
#...in retrospect, i think i coud just use sum.colorcast, above.
#head(sum.colorcast)

Combo=read.csv("NN_SI_Combo.csv")

RewardsPerTreatment=sum.colorcast %>%
  mutate(BluePreference=blue/(blue+not.blue)) %>%
  group_by(pre.post,Neonic,Treatment_Type) %>%
  summarise(AvgBluePreference=mean(BluePreference), SdBluePreference=sd(BluePreference), SumBlueRewards=sum(blue), SumTotalRewards=sum(blue+not.blue)) %>%
  filter (SumBlueRewards>0)

RewardsPerTreatment1=left_join(sum.colorcast,Combo,by=c("Neonic","Treatment_Type"))
RewardsPerTreatment2= RewardsPerTreatment1 %>%
  mutate(BluePreference=blue/(blue+not.blue))  %>%
  group_by(pre.post,Combo, Neonic, Treatment_Type) %>% 
  mutate(N=n()) %>%
  group_by(pre.post,Combo,N, Neonic, Treatment_Type) %>%      #i did this to keep N as a column
  summarise(AvgBluePreference=mean(BluePreference), SdBluePreference=sd(BluePreference), SumBlueRewards=sum(blue), SumTotalRewards=sum(blue+not.blue)) %>%
  filter (SumBlueRewards>0)

#########


#calculating confidence intervals
require(binom)
RpTconfint=binom.confint(x=RewardsPerTreatment2$SumBlueRewards, n=RewardsPerTreatment2$SumTotalRewards, conf.level=.95, methods = "agresti-coull")
RpTconfint
#selecting the upper and lower bounds from the conf int table to add to RewardsPerTreatment
RpTUpLow=select(RpTconfint, lower, upper )
RewardsPerTreatment2=bind_cols(RewardsPerTreatment2,RpTUpLow)
index = which(is.na(RewardsPerTreatment2$Combo))
RewardsPerTreatment2 = RewardsPerTreatment2[-index,]




#plot 2- berry's aesthetic

pd <- position_dodge(width = 0.1)

plot2 <- ggplot(RewardsPerTreatment2, aes(color = Combo, y = AvgBluePreference, x = pre.post))
plot2 <- plot2 + geom_point(position=pd) + geom_line(aes(group = Combo), position=pd) 
plot2 = plot2 + labs(x="Pre v Post", y="Proportion of Visits to Blue Flowers")
plot2= plot2 + theme_classic() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + coord_cartesian(xlim = c(1.4,2.2), ylim = c(0.1,1.0))


plot2

#offsetting the error bars example from stack exchange
#pd <- position_dodge(width = 0.4)

#ggplot(YearlyDensity, aes(x = Year, y = mean, colour = Station, group = Station)) +
#  geom_errorbar(aes(ymin = mean-se, ymax = mean+se),
#                colour = "black", width = 0.2, position = pd) +
#  geom_line(size = .8, position = pd) +
#  geom_point(size = 4, shape = 18, position = pd) +

#mdf$variable <- as.numeric(as.character(mdf$variable))
RewardsPerTreatment2$Combo <-as.character(as.numeric(RewardsPerTreatment2$Combo))

pd <- position_dodge(width = 0.1)

plot3 <- ggplot(RewardsPerTreatment2, aes(group=Combo, color = Combo, y = AvgBluePreference, x = pre.post)) + geom_point( position=pd,size=1) + geom_line(aes(group = Combo), position=pd) + labs(x="Pre v Post", y="Proportion of Visits to Blue Flowers") + theme_minimal() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + coord_cartesian(xlim = c(1.4,1.9), ylim = c(0.1,1.0))+ scale_color_hue(labels=c("NN honest", "NN misleading", "NN control", "naive honest", "naive misleading", "naive control"))
  
  
  
#scale_color_brewer(palette ="Set1" ) + scale_fill_discrete(name="Treatment", labels=c("NN honest", "NN misleading", "NN control", "naive honest", "naive misleading", "naive control"))

plot3


#Analyzing Bee Reward Order

template:
sis32=sis3 %>%
  group_by(Sister) %>%
  mutate(Order2=1:n())
  
There are NAs coming up in the ordered data and the switch data which follows. That's recording a tag (for 1B-29 and 60-27) that wasn't part of any treatment or colony types. I think it's maybe a short-term tester tag? Regardless, it's two "bees"" that aren't anywhere on the Bombus ID data spreadsheet (which is hand-typed to include all bees which are tagged). So I'm deleting them.


Had as issue with NAs popping up in ways that don't make sense (e.g. as a factor level for Social_Cue, when in reality are social_cue levels are accounted for.)

possible solution from internet: https://forcats.tidyverse.org/reference/fct_explicit_na.html

f1 <- factor(c("a", "a", NA, NA, "a", "b", NA, "c", "a", "c", "b"))
fct_count(f1)
#> # A tibble: 4 x 2
#>   f         n
#>   <fct> <int>
#> 1 a         4
#> 2 b         2
#> 3 c         2
#> 4 NA        3

f2 <- fct_explicit_na(f1)
fct_count(f2)
#> # A tibble: 4 x 2
#>   f             n
#>   <fct>     <int>
#> 1 a             4
#> 2 b             2
#> 3 c             2
#> 4 (Missing)     3




```{r}

OrderableData=all.colordata %>%
  select(bee, Neonic, Social_Cue, reward.x, color, Day, Colony, t.forage)
OrderableData=OrderableData %>%
  filter(reward.x==1) 
OrderableData=OrderableData %>%
  arrange(bee, Day, t.forage) %>%
  group_by(bee, Day) %>%
  mutate(Order=1:n())




Check5=filter(OrderableData, Colony=="4")

#Separate day 1 and day 2

Day1order=all.colordata %>%
  select(bee, Neonic, Social_Cue, reward.x, color, Day, Colony, t.forage) %>%
  filter(reward.x==1, Day=="treatment") %>%
  arrange(bee, t.forage) %>%
  group_by(bee) %>%
  mutate(Order=1:n())


#Day1order[is.na(Day1order)] <-"what"

#Full.Test1 =filter(Full.Test1, bee !="A2-25-66-01-0B-00-12-E0")

Day1order=filter(Day1order, bee != "1B-29-66-01-0B-00-12-E0")
Day1order=filter(Day1order, bee != "60-27-66-01-0B-00-12-E0")

Day2order=all.colordata %>%
  select(bee, Neonic, Social_Cue, reward.x, color, Day, Colony, t.forage) %>%
  filter(reward.x==1, Day=="test") %>%
  arrange(bee, t.forage) %>%
  group_by(bee) %>%
  mutate(Order=1:n())

  
#have to melt data again to make graph
Meltable.Day1order= Day1order %>%
  ungroup() %>%
  select(Order, Neonic, Social_Cue, color) %>%
  group_by(Neonic, Social_Cue, Order) %>%
  arrange(Neonic, Social_Cue, Order) %>%
  count(Neonic, Social_Cue, color, Order)

Meltable.Day1order$Neonic<- fct_explicit_na(Meltable.Day1order$Neonic)
Meltable.Day1order$Social_Cue<- fct_explicit_na(Meltable.Day1order$Social_Cue)

Meltable.Day1order= filter(Meltable.Day1order, Neonic != "(Missing)")


Spread.Day1order=spread(data=Meltable.Day1order, key=color, value=n)
Spread.Day1order$blue.treatment[is.na(Spread.Day1order$blue.treatment)] <- 0 
Spread.Day1order$green.treatment[is.na(Spread.Day1order$green.treatment)] <- 0

Spread.Day1order=mutate(Spread.Day1order,BluePref=blue.treatment/(blue.treatment+green.treatment))

#Somehow in the spread I created a bunch of rows that were NA for treament and neonic. However, all of my levels for all of those factors are present, so I'm gonna assume that's junk right now.

Meltable.Day2order= Day2order %>%
  ungroup() %>%
  select(Order, Neonic, Social_Cue, color) %>%
  group_by(Neonic, Social_Cue, Order) %>%
  arrange(Neonic, Social_Cue, Order) %>%
  count(Neonic, Social_Cue, color, Order)

Meltable.Day2order$Neonic<- fct_explicit_na(Meltable.Day2order$Neonic)
Meltable.Day2order$Social_Cue<- fct_explicit_na(Meltable.Day2order$Social_Cue)

Meltable.Day2order= filter(Meltable.Day2order, Neonic != "(Missing)")

Spread.Day2order=spread(data=Meltable.Day2order, key=color, value=n)
Spread.Day2order$blue.test[is.na(Spread.Day2order$blue.test)] <- 0 
Spread.Day2order$violet.test[is.na(Spread.Day2order$violet.test)] <- 0

Spread.Day2order=mutate(Spread.Day2order, BluePref=blue.test/(blue.test+violet.test))

Day2OrderPlot=ggplot(data=Spread.Day2order, aes(group=Social_Cue, color=Social_Cue, x=Order, y=BluePref)) + facet_grid(.~Neonic) + geom_point(position=pd, size=1) + geom_line(aes(group=Social_Cue), position=pd) +theme_classic()
Day2OrderPlot

SameDay2OrderPlot=ggplot(data=Spread.Day2order, aes(group=Social_Cue, color=Social_Cue, x=Order, y=BluePref)) + facet_grid(.~Neonic) + geom_point(position=pd, size=1) + geom_line(aes(group=Social_Cue), position=pd) +theme_classic()+ coord_cartesian(xlim = c(1,5))+ labs(title="Bees' Preference for Blue Flowers on Day 2, Choices 1-5")
SameDay2OrderPlot
#there are also NAs where there should be 0s. changing those...

#Spread.Day1order[is.na(Spread.Day1order)] <-0
#Spread.Day1order.Clean=slice(Spread.Day1order, 1:83)
#index1 = which(is.na(Spread.Day1order.Clean))
#Spread.Day1order.Clean = Spread.Day1order.Clean[-index1,]



Day1OrderPlot=ggplot(data=Spread.Day1order, aes(group=Social_Cue, color=Social_Cue, x=Order, y=BluePref)) + facet_grid(.~Neonic) + geom_point(position=pd, size=1) + geom_line(aes(group=Social_Cue), position=pd) +theme_classic()  + labs(title="Bees' Preference for Blue Flowers on Day 1")+ geom_hline(yintercept=0.5,linetype="dashed", color = "black")+scale_color_manual(values = c(control="darkgoldenrod", honest="cornflowerblue", misleading="darkolivegreen4"))
Day1OrderPlot

#same plot as above, but artificialy limited to the average number of visits that at leat 10 bees made (i.e. up to 6 on x axis)

SameDay1OrderPlot=ggplot(data=Spread.Day1order, aes(group=Social_Cue, color=Social_Cue, x=Order, y=BluePref)) + facet_grid(.~Neonic) + geom_point(position=pd, size=1) + geom_line(aes(group=Social_Cue), position=pd) +theme_classic() + coord_cartesian(xlim = c(1,5))+ labs(title="Bees' Preference for Blue Flowers on Day 1, Choices 1-5")+ geom_hline(yintercept=0.5,linetype="dashed", color = "black")+scale_color_manual(values = c(control="darkgoldenrod", honest="cornflowerblue", misleading="darkolivegreen4"))
SameDay1OrderPlot


#Plotting individual bees
#Order.colordata=full_join(1OrderableData, color.treatments, by="color")
Allbee.Order.Day1=select(Day1order, bee, Neonic, Social_Cue, Order,color)
#index = which(is.na(Allbee.Order.Day1))
#Allbee.Order.Day1 = Allbee.Order.Day1[-index,]


AllbeeDay1Plot=ggplot(data=Allbee.Order.Day1, aes(group=bee, color=bee, x=Order, y=color)) + facet_grid(Neonic~Social_Cue) + geom_point( size=1) + geom_line(aes(group=bee)) +theme_classic()+ guides(color="none")
#AllbeeDay1Plot
#+ coord_cartesian(xlim = c(1,5))
#herehere
```


```{r}
Day1orderM=as.matrix(Day1order)
Switch=c("Start")
for(i in 2:nrow(Day1orderM)){
             if(Day1orderM[i,1] != Day1orderM[i-1,1]) Switch[i] = "Start" else if(Day1orderM[i,5] != Day1orderM[i-1,5]) Switch[i] = "Switch" else Switch[i] = "Same"
}
Day1orderS=cbind(Switch, Day1orderM)
Day1orderSwitch=as.data.frame(Day1orderS)



#Preparing Data to plot
SMeltable.Day1order=Day1orderSwitch %>%
  ungroup() %>%
  select(Switch, Neonic, Social_Cue) %>%
  group_by(Neonic, Social_Cue, Switch) %>%
  arrange(Neonic, Social_Cue, Switch) %>%
  count(Neonic, Social_Cue, Switch) 

Spread.SwitchDay1=spread(data=SMeltable.Day1order, key=Switch, value=n)
Spread.SwitchDay1=filter(Spread.SwitchDay1, !is.na(Neonic))
Spread.SwitchDay1=Spread.SwitchDay1 %>%
  mutate(SwitchPercent=Switch/(Switch+Same+Start)) %>%
  mutate(SamePercent=Same/(Switch+Same+Start)) %>%
  mutate(Total=Switch+Same+Start)



SwitchDay1Plot=ggplot(data=Spread.SwitchDay1, aes(x=Neonic, group= Social_Cue, color=Social_Cue, fill=Social_Cue, y=SwitchPercent)) + geom_col(position = position_dodge()) + theme_classic() 
SwitchDay1Plot
#has no confidence intervals, hold on.

#calculating confidence intervals
Day1SwitchConfInt=binom.confint(x=Spread.SwitchDay1$Switch, n=Spread.SwitchDay1$Total, conf.level=.95, methods="agresti-coull")
Day1SwitchConfIntSelect=select(Day1SwitchConfInt, lower, upper)
Spread.SwitchDay1=bind_cols(Spread.SwitchDay1, Day1SwitchConfIntSelect)

#Plotting again, but better this time
#plot3 <- ggplot(RewardsPerTreatment2, aes(group=Combo, color = Combo, y = AvgBluePreference, x = pre.post)) + geom_point( position=pd,size=1) + geom_line(aes(group = Combo), position=pd) + labs(x="Pre v Post", y="Proportion of Visits to Blue Flowers") + theme_minimal()  + coord_cartesian(xlim = c(1.4,1.9), ylim = c(0.1,1.0))+ scale_color_hue(labels=c("NN honest", "NN misleading", "NN control", "naive honest", "naive misleading", "naive control"))

Day1SwitchPlot=ggplot(data=Spread.SwitchDay1, aes(x=Neonic, group= Social_Cue, color=Social_Cue, fill=Social_Cue, y=Switch/Total)) + geom_point(position=pd, size=1) + theme_classic() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + labs(title="Proportion of visits where bee switched to the other flower")+scale_color_manual(values = c(control="darkgoldenrod", honest="cornflowerblue", misleading="darkolivegreen4"))

Day1SwitchPlot

#How about the proportion of visits where bees sample the green flower, even after they know that blue is better?
    #I would need the number of visits to green after a bee has been to both blue and green.
```

#First reward, no Neonics
```{r}
FirstFlowerDay1=Spread.Day1order %>%
  filter(Order==1, Neonic=="n") %>%
  mutate(Allfirsts=sum(blue.treatment+green.treatment))

FirstFlowerDay2=Spread.Day2order %>%
  filter(Order==1, Neonic=="n") %>%
  mutate(Allfirsts=sum(blue.test+violet.test))


#Confidence Intervals
FirstFlower.Day1.confint=binom.confint(x=FirstFlowerDay1$blue.treatment, n=FirstFlowerDay1$Allfirsts, conf.level=.95, methods = "agresti-coull")
FirstFlower.Day1.confint
#selecting the upper and lower bounds from the conf int table to add to RewardsPerTreatment
FirstFlower.Day1.confint.uplow=select(FirstFlower.Day1.confint, lower, upper, mean )
FirstFlowerDay1=bind_cols(FirstFlowerDay1,FirstFlower.Day1.confint.uplow)

FirstFlower.Day2.confint=binom.confint(x=FirstFlowerDay2$blue.test, n=FirstFlowerDay1$Allfirsts, conf.level=.95, methods = "agresti-coull")
FirstFlower.Day2.confint
#selecting the upper and lower bounds from the conf int table to add to RewardsPerTreatment
FirstFlower.Day2.confint.uplow=select(FirstFlower.Day2.confint, lower, upper, mean )
FirstFlowerDay2=bind_cols(FirstFlowerDay2,FirstFlower.Day2.confint.uplow)

FirstFlowerDay1Plot<- ggplot(FirstFlowerDay1, aes(y = BluePref, x = Social_Cue)) + geom_point( position=pd,size=3) + labs(x="Social Cue", y="Proportion of Bees that First Visited Blue Flower", title="Proportion of Foragers that Chose Blue Flower on First Visit to Flower on Day 1") + theme_classic() + scale_color_hue() + geom_hline(yintercept=0.5,linetype="dashed", color = "black")+ geom_errorbar(aes(ymin=lower, ymax=upper, width=.1))

#FirstFlowerDay1Plot

FirstFlowerDay2Plot<- ggplot(FirstFlowerDay2, aes(y = BluePref, x = Social_Cue)) + geom_point( position=pd,size=3) + labs(x="Social Cue", y="Proportion of Bees that First Visited Blue Flower", title="Proportion of Foragers that Chose Blue Flower on First Visit to Flower on Day 2") + theme_classic() + scale_color_hue() + geom_hline(yintercept=0.5,linetype="dashed", color = "black")+ geom_errorbar(aes(ymin=lower, ymax=upper, width=.1))

#FirstFlowerDay2Plot

#combining both data sets so that these graphs can be two facets of the same figure
#add a column for day of trials (1 or 2)
#change column names to blue and not.blue
Day1=c(1,1,1)
FirstFlowerDay1= FirstFlowerDay1 %>%
  add_column(Day=Day1)

FirstFlowerDay1=FirstFlowerDay1 %>%
    mutate(blue=blue.treatment) %>%
  mutate(not.blue=green.treatment)

Day2=c(2,2,2)
FirstFlowerDay2=FirstFlowerDay2 %>%
  add_column(Day=Day2)

FirstFlowerDay2=FirstFlowerDay2 %>%
    mutate(blue=blue.test) %>%
  mutate(not.blue=violet.test)

FirstFlowerBothDays=bind_rows(FirstFlowerDay1, FirstFlowerDay2)

factlabelsday=c("Day 1- Treatment", "Day 2- Test")
names(factlabelsday) = c(1,2)


FirstFlowerPlot<- ggplot(FirstFlowerBothDays, aes(y = BluePref, x = Social_Cue, color=Social_Cue)) + geom_point( position=pd,size=3) + labs(x="Social Cue", y="Proportion of Bees that Visited Blue Flower First", title="Bees' First Choice of Flower") + theme_classic() + scale_color_hue() + geom_hline(yintercept=0.5,linetype="dashed", color = "black")+ geom_errorbar(aes(ymin=lower, ymax=upper, width=.1))+ facet_grid(.~Day, labeller=labeller(Day = factlabelsday)) + scale_fill_discrete(name = "Social Cue Treatment")+scale_color_manual(values = c(control="darkgoldenrod", honest="cornflowerblue", misleading="darkolivegreen4"))

FirstFlowerPlot



#Glmm's
firstDay1model=glm(BluePref~Social_Cue, family=binomial, data=FirstFlowerDay1)
summary(firstDay1model)
#Social_Cuehonest       0.2513     2.9948   0.084    0.933
#Social_Cuemisleading  -1.0136     2.9203  -0.347    0.729
FirstFlowerDay1$Social_Cue=factor(FirstFlowerDay1$Social_Cue, levels(factor(FirstFlowerDay1$Social_Cue))[c(3,1,2)])
firstDay1model2=glm(BluePref~Social_Cue, family=binomial, data=FirstFlowerDay1)
summary(firstDay1model2)
#Social_Cuecontrol    1.014      2.920   0.347    0.729
#Social_Cuehonest     1.265      2.982   0.424    0.671


firstDay2model=glm(BluePref~Social_Cue, family=binomial, data=FirstFlowerDay2)
summary(firstDay2model)
#Social_Cuehonest     -0.13513    2.83408  -0.048    0.962
#Social_Cuemisleading  0.19956    2.83325   0.070    0.944
FirstFlowerDay2$Social_Cue=factor(FirstFlowerDay2$Social_Cue, levels(factor(FirstFlowerDay2$Social_Cue))[c(3,1,2)])
firstDay2model2=glm(BluePref~Social_Cue, family=binomial, data=FirstFlowerDay2)
summary(firstDay2model2)
#Social_Cuecontrol  -0.1996     2.8332  -0.070    0.944
#Social_Cuehonest   -0.3347     2.8384  -0.118    0.906

# reference text
preNaive=all.colorcast %>%
  filter(pre.post=="pre") %>%
  filter(Neonic=="n")

preNaive.glmm=glmer(cbind(blue,not.blue)~Social_Cue+(1|Colony/bee), family=binomial, data=preNaive)
summary(preNaive.glmm)
Anova(preNaive.glmm)
#misleading is sig diff from control p =0.0165, honest is not sig dif p=0.1408

postNaive=all.colorcast %>%
  filter(pre.post=="post") %>%
  filter(Neonic=="n")

postNaive.glmm=glmer(cbind(blue,not.blue)~Social_Cue+(1|Colony/bee), family=binomial, data=postNaive)
summary(postNaive.glmm)
Anova(postNaive.glmm)
#misleading p=0.156, honest p=0.918


#can i relevel the factors?
#all.RewardsPerTreatment1$Social_Cue = factor(all.RewardsPerTreatment1$Social_Cue, levels(factor(all.RewardsPerTreatment1$Social_Cue))[c(1,3,2)])

preNaive$Social_Cue=factor(preNaive$Social_Cue, levels(factor(preNaive$Social_Cue))[c(3,1,2)])
  
preNaive2.glmm=glmer(cbind(blue,not.blue)~Social_Cue+(1|Colony/bee), family=binomial, data=preNaive)
summary(preNaive2.glmm)
#control(p=0.016454) and honest(p=0.000153) both significantly different from misleading

postNaive$Social_Cue=factor(postNaive$Social_Cue, levels(factor(postNaive$Social_Cue))[c(3,1,2)])

postNaive2.glmm=glmer(cbind(blue,not.blue)~Social_Cue+(1|Colony/bee), family=binomial, data=postNaive)
summary(postNaive2.glmm)
#neither is significant control p=0.156, honest p=0.202

```


#What if all the flowers are blue?
I ran a few rounds of data collection in the foraging chamber in which the flowers were always blue. I did this becuase Donna Maney brought up at my committe meeting that it's possible that bees aren't learning flower color, but are instead learning something about the position of the rewarding and not-rewarding flowers. Michal suggested I collect data with all blue flowers (no neonics, yes social cues) to address this. My data colelction got cut off by foraging chamber woes followed by David's data collection followed by COVID. So. This is what I have.


```{r}
#importing and naming each data set
bTr.1347=read.csv("foragingdata_2020.2.28.1347.csv")
colnames(bTr.1347) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

bTr.1440=read.csv("foragingdata_2020.2.28.1440.csv")
colnames(bTr.1440) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

bTr.1536=read.csv("foragingdata_2020.2.28.1536.csv")
colnames(bTr.1536) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

bTr.1613=read.csv("foragingdata_2020.2.28.1613.csv")
colnames(bTr.1613) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

bTr.1717=read.csv("foragingdata_2020.2.28.1717.csv")
colnames(bTr.1717) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

bTe.1321=read.csv("foragingdata_2020.2.29.1321.csv")
colnames(bTe.1321) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

bTe.1358=read.csv("foragingdata_2020.2.29.1358.csv")
colnames(bTe.1358) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

bTe.1434=read.csv("foragingdata_2020.2.29.1434.csv")
colnames(bTe.1434) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

bTe.1244=read.csv("foragingdata_2020.2.29.1244.csv")
colnames(bTe.1244) = c("date", "t.day", "flower", "bee", "t.forage", "reward")

bTe.1208=read.csv("foragingdata_2020.2.29.1208.csv")
colnames(bTe.1208) = c("date", "t.day", "flower", "bee", "t.forage", "reward")


#importing the data set that describes the shapes of flowers, treatment types, etc.
    #this file has a formula for changing space-separated bee id's into dash-separated bee id names
bee.info.blue=read.csv("BombusIDallblue.csv")

#knitting together data sets into "treatment" files 
bFull.Treatment1=rbind(bTr.1347,bTr.1440,bTr.1536,bTr.1613,bTr.1717)

#knitting together data sets into "test" files
bFull.Test1=rbind(bTe.1321,bTe.1358,bTe.1434,bTe.1244,bTe.1208)


#removing tester flower from both data sets
bFull.Treatment1 =filter(bFull.Treatment1, bee !="CE-28-66-01-0B-00-12-E0")
bFull.Treatment1 =filter(bFull.Treatment1, bee !="D9-28-66-01-0B-00-12-E0")
bFull.Test1 =filter(bFull.Test1, bee !="CE-28-66-01-0B-00-12-E0")
bFull.Test1 =filter(bFull.Test1, bee !="D9-28-66-01-0B-00-12-E0")


#counting visits and rewards during Treatment runs
#tbl_df(Full.Treatment1)
bTotal.visits=count(bFull.Treatment1, bee)
#Total.visits
bTotal_Rewards=bFull.Treatment1%>%
  group_by(bee) %>%
  summarise(Rewards=sum(reward))
#Total_Rewards  

#Total_Rewards
bTotal_RV=left_join(bTotal.visits, bTotal_Rewards, by="bee")
index = which(is.na(bTotal_RV$Rewards))
bTotal_RV = bTotal_RV[-index,]
colnames(bTotal_RV)=c("bee", "Treatment.Visits", "Treatment.Rewards")
#Total_RV
bAvg.Visits=summarise(bTotal_RV, Treatment.visits=mean(Treatment.Visits), Treatment.reward=mean(Treatment.Rewards))
#Avg.Visits


#Counting visits and rewards during test runs
#tbl_df(Full.Test1)
bTotal.visitsT=count(bFull.Test1, bee)
#Total.visitsT
bTotal_RewardsT=bFull.Test1%>%
  group_by(bee) %>%
  summarise(Rewards=sum(reward))
#Total_RewardsT  

#Total_RewardsT
bTotal_RV_T=left_join(bTotal.visitsT, bTotal_RewardsT, by="bee")
index = which(is.na(bTotal_RV_T$Rewards))
bTotal_RV_T = bTotal_RV_T[-index,]
colnames(bTotal_RV_T)=c("bee", "Test.Visits", "Test.Rewards")
#Total_RV_T
bAvg.VisitsT=summarise(bTotal_RV_T, Test.visits=mean(Test.Visits), Test.reward=mean(Test.Rewards))
#Avg.VisitsT

bAllVisits=left_join(bTotal_RV,bTotal_RV_T, by="bee") %>%
  filter(Test.Visits>0)
#AllVisits
bAvg.AllVisits=cbind(bAvg.Visits, bAvg.VisitsT)
bAvg.AllVisits


#BeeDataOrig
#tbl_df(BeeData)
#Simple_BeeData=
 # slice(BeeData,41:109) %>%
#  group_by(bee)

bBeeData=full_join(bAllVisits, bee.info.blue, by="bee")
bBeeData =filter(bBeeData, bee !="A2-25-66-01-0B-00-12-E0")
bBeeData[is.na(bBeeData)] <- 0 
#BeeData
select(bBeeData, bee:Treatment_Type) %>%
  slice(1:50) %>%
  group_by(Treatment_Type) %>%
  summarise(AvgTreatVisits=mean(Treatment.Visits), AvgTreatRewards=mean(Treatment.Rewards),AvgTestVisits=mean(Test.Visits), AvgTestRewards=mean(Test.Rewards))

bFull.Data=rbind(bFull.Treatment1, bFull.Test1)
bFull.Data=filter(bFull.Data, bee !="A2-25-66-01-0B-00-12-E0")
#making a little data frame to assign Treatment and Test to the calendar dates
Day=c("treatment", "test")
date=c("2020.2.28", "2020.2.29")     
bdaydate=cbind(Day, date)
bdaydate=as.data.frame(bdaydate)


colors=read.csv("Flower color data Summer SI learning envt trials.csv")
names(colors) <- c("flower", "reader", "Day", "color", "reward")
#colors

#need to join dayDate to full trial, then join treatment types and colors to all of that

bFull.Data=left_join(bFull.Data,bdaydate,by="date") 
#%>% select(-Days)
colnames(bFull.Data)[colnames(bFull.Data)=="Day.x"] <- "Day"


#adding in treatment types
bFull.Data.Treatments=full_join(bFull.Data, bee.info.blue, by="bee")

#adding in colors
bFull.Data.Colorss=full_join(bFull.Data.Treatments,colors, by=c("flower", "Day"))
bFull.Data.Colors= bFull.Data.Colorss[1:23047,]

#bFull.Data.Colors has all of the visit data with treatments, colors, etc. It has no NAs becuase I resolved those along the way.

#####################

bFull.Data.All= select(bFull.Data.Colors, bee, Neonic, Treatment_Type, reward.x, color, Day, Colony)


#Full.Data.All focuses in on columns of interest. Following data manip moves from an "each bee each visit" view to groupings of treatments etc.

#sum of rewards bees got from each color
bcolor.visits=group_by(bFull.Data.All, color) %>%
  summarise(Rewards=sum(reward.x))   
index = which(is.na(bcolor.visits))
bcolor.visits = bcolor.visits[-index,]
#head(color.visits)

#i made a table of how to name the colors in last round of analysis, here's a reminder of what it is:
bcolor.treatments=read.csv("bcolor.treatments.csv")
bcolor.treatments=tbl_df(bcolor.treatments)

bcolordata=full_join(bFull.Data.All, bcolor.treatments, by="color")
#colordata
#summarizing that full data by summing up the rewards for each treatment type
bsum.colordata=bcolordata  %>% 
  group_by(Neonic,Treatment_Type, color, Colony) %>% 
  summarise(sums=sum(reward.x))
index = which(is.na(bsum.colordata))
bsum.colordata = bsum.colordata[-index,]

#spreading and melting data...
btreatment.summaries=spread(bsum.colordata, color, sums)
# the NAs in the above spreadsheet are 0s

bsum.colordata=select(bcolordata, Colony, bee, Neonic, Treatment_Type, reward.x, pre.post, new.reward)
#sum.colordata
#sum.colordata is the rawest data that shows all of and each bee-flower visit.
#colorcast=dcast(sum.colordata, bee + Treatment_Type+pre.post~reward.x+new.color, fun.aggregate = sum)
#trying to just cast without melting did not work, even when I removes "reward.x"


bsum.colordata$Colony <-as.character(as.numeric(bsum.colordata$Colony))



bsum.colormelt=melt(bsum.colordata)
#sum.colormelt


#casting data
bsum.colorcast=dcast(bsum.colormelt, bee + Colony+ Neonic+ Treatment_Type+pre.post~new.reward, fun.aggregate = sum)
#sum.colorcast
head(bsum.colorcast)
summary(bsum.colorcast)



#GLMing data
allblueGLM=glmer(cbind(RewardDay1, Not.RewardDay1)~pre.post*Treatment_Type+(1|Colony/bee), family=binomial, data=bsum.colorcast)

summary(allblueGLM)
Anova(allblueGLM)



#plotting

ball.RewardsPerTreatment=bsum.colorcast %>%
  mutate(RewardingSpacePreference=RewardDay1/(RewardDay1+Not.RewardDay1)) %>%
  group_by(pre.post,Treatment_Type) %>%
  summarise(AvgRewardSpacePreference=mean(RewardingSpacePreference), SdRewardSpacePreference=sd(RewardingSpacePreference), SumRewardSpaceRewards=sum(RewardDay1), SumTotalRewards=sum(RewardDay1+Not.RewardDay1)) %>%
  filter (SumRewardSpaceRewards>0)

#Confidence Intervals
ball.RpTconfint=binom.confint(x=ball.RewardsPerTreatment$SumRewardSpaceRewards, n=ball.RewardsPerTreatment$SumTotalRewards, conf.level=.95, methods = "agresti-coull")
ball.RpTconfint
#selecting the upper and lower bounds from the conf int table to add to RewardsPerTreatment
ball.RpTUpLow=select(ball.RpTconfint, lower, upper, mean )
ball.RewardsPerTreatment=bind_cols(ball.RewardsPerTreatment,ball.RpTUpLow)

class(ball.RewardsPerTreatment$pre.post)
ball.RewardsPerTreatment$pre.post = factor(ball.RewardsPerTreatment$pre.post, levels(factor(ball.RewardsPerTreatment$pre.post))[c(2,1)])

ball.RewardsPerTreatment$Treatment_Type = factor(ball.RewardsPerTreatment$Treatment_Type, levels(factor(ball.RewardsPerTreatment$Treatment_Type))[c(1,3,2)])

Day12labs <- c("Day 1", "Day 2")



ball.plot <- ggplot(ball.RewardsPerTreatment, aes(group=Treatment_Type, color = Treatment_Type, y = SumRewardSpaceRewards/SumTotalRewards, x = pre.post)) + geom_point( position=pd,size=3) + geom_line(aes(group = Treatment_Type), size=3, position=pd) + labs(x="Day of Foraging", y="Proportion of Visits to Day1 Rewarding Flower", title="Proportion of Visits to Each of Two Blue Flowers")+ scale_x_discrete(labels= Day12labs) + theme_classic() + geom_errorbar(aes(ymin=lower, ymax=upper, width=.1), position=pd) + coord_cartesian(xlim = c(1.4,1.9), ylim = c(0.3,0.9))+ scale_color_hue() + geom_hline(yintercept=0.5,linetype="dashed", color = "black") + scale_color_manual(values = c(c="darkgoldenrod", m="darkolivegreen4", h="cornflowerblue"), name="Social Cue", labels=c("Control", "Misleading", "Honest"))

ball.plot
```

G tests for all-blue trials
```{r}


#Berry look here for Bee Paper 1#
#G tests for all-blue trials



bGsumtest.prep= bsum.colorcast %>%
  group_by(Treatment_Type, pre.post) %>%
  summarise(sumDay1RewFlower=sum(RewardDay1), sumDay1NotRewFlower=sum(Not.RewardDay1))%>%
  mutate(RewDay1Prop=sumDay1RewFlower/(sumDay1RewFlower+sumDay1NotRewFlower)) %>%
  mutate(RewDay1PropSE=std.error(RewDay1Prop))

BluePropV=as.vector(Gsumtest.prep$BlueProp)
BluePropV

bGsummatrprep=select(bGsumtest.prep, sumDay1RewFlower, sumDay1NotRewFlower)
bGsummatrprep
bgsummatr=as.matrix(bGsummatrprep, header=TRUE)
bgsummatr=bgsummatr[,c(2,3)]
class(bgsummatr)
bgsummatr



bobCpo=c(49,43)
bobCpr=c(75,19)
bobHpo=c(28,44)
bobHpr=c(51,27)
bobMpo=c(25,24)
bobMpr=c(42,23)
expected=c(0.5,0.5)
G.test(bobCpo, expected)
#G =0.39158      , df = 1, p-value =0.5315 
G.test(bobCpr, expected)
#G =35.684      , df = 1, p-value =2.3e-09 
G.test(bobHpo, expected)
#G =3.584     , df = 1, p-value = 0.05829
G.test(bobHpr, expected)
#G =7.5058      , df = 1, p-value =0.0615 
G.test(bobMpo, expected)
#G =0.02041      , df = 1, p-value =0.8864 
G.test(bobMpr, expected)
#G =5.6358      , df = 1, p-value =0.0176 

```

#How many all blue bees?
```{r}
#overall
btotalbees=count(bcolordata, bee)
#btotalbees=28 rows


#control 
bControl= bcolordata %>% 
  filter(Treatment_Type=="c") %>%
  count(bee)
#bControl=14 rows



#honest, no
bHonest= bcolordata %>% 
  filter(Treatment_Type=="h") %>%
  count(bee)
#HonestNoPest = 6


#miselading
bMisleading= bcolordata %>% 
  filter(Treatment_Type=="m") %>%
  count(bee)
#MislNoPest=7

```


#"posthoc" glmms for bee paper 1
don't call these posthoc comparisons, just report that "I divided the data to assess differences in training groups in the pre and post condition. we conducted separate followup anaylses byt training tpes. specicaflly, in the pre condiditon, we compared each of the social info treatments to the control andlaso to the honest (to see if theyre really following social cues). In the post data, we want to see if mislead bees behave differently from the other two groups."
-berry says to do separate glmms, one for pre and one for post (so social info cue is the only variable, and control is the reference variable. I'll get two p values (one for honest and one for misleading, each is compared to control)(ideally both contrasts will be significant). next, for the social cue factor, run the levels (or relevel) command and say ref=misleading- so then the next model will compare control and honest each to misleading. 


```{r}

preNaive=all.colorcast %>%
  filter(pre.post=="pre") %>%
  filter(Neonic=="n")

preNaive.glmm=glmer(cbind(blue,not.blue)~Social_Cue+(1|Colony/bee), family=binomial, data=preNaive)
summary(preNaive.glmm)
Anova(preNaive.glmm)
#misleading is sig diff from control p =0.0165, honest is not sig dif p=0.1408

postNaive=all.colorcast %>%
  filter(pre.post=="post") %>%
  filter(Neonic=="n")

postNaive.glmm=glmer(cbind(blue,not.blue)~Social_Cue+(1|Colony/bee), family=binomial, data=postNaive)
summary(postNaive.glmm)
Anova(postNaive.glmm)
#misleading p=0.156, honest p=0.918


#can i relevel the factors?
#all.RewardsPerTreatment1$Social_Cue = factor(all.RewardsPerTreatment1$Social_Cue, levels(factor(all.RewardsPerTreatment1$Social_Cue))[c(1,3,2)])

preNaive$Social_Cue=factor(preNaive$Social_Cue, levels(factor(preNaive$Social_Cue))[c(3,1,2)])
  
preNaive2.glmm=glmer(cbind(blue,not.blue)~Social_Cue+(1|Colony/bee), family=binomial, data=preNaive)
summary(preNaive2.glmm)
#control(p=0.016454) and honest(p=0.000153) both significantly different from misleading

postNaive$Social_Cue=factor(postNaive$Social_Cue, levels(factor(postNaive$Social_Cue))[c(3,1,2)])

postNaive2.glmm=glmer(cbind(blue,not.blue)~Social_Cue+(1|Colony/bee), family=binomial, data=postNaive)
summary(postNaive2.glmm)
#neither is significant control p=0.156, honest p=0.202

```











```{r}
# Generate a plot of color names which R knows about.
#++++++++++++++++++++++++++++++++++++++++++++
# cl : a vector of colors to plots
# bg: background of the plot
# rot: text rotation angle
#usage=showCols(bg="gray33")
showCols <- function(cl=colors(), bg = "gray",
                     cex = 0.75, rot = 30) {
    m <- ceiling(sqrt(n <-length(cl)))
    length(cl) <- m*m; cm <- matrix(cl, m)
    require("grid")
    grid.newpage(); vp <- viewport(w = .92, h = .92)
    grid.rect(gp=gpar(fill=bg))
    grid.text(cm, x = col(cm)/m, y = rev(row(cm))/m, rot = rot,
              vp=vp, gp=gpar(cex = cex, col = cm))
}

showCols(cl= colors(), bg="white", rot=30, cex=0.5)
```












